---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# SSACHR: Serial Sexual Assault Study Criminal History Records Paper
<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/cstatops)](https://CRAN.R-project.org/package=SSAlvmm)
<!-- badges: end -->

This package and corresponding GitHub repository are intended to enhance the
reproducibility of a research paper. The principal investigator for the study is
Dr. Rebecca Campbell (Professor, Department of Psychology, Michigan State
University).  The paper will present descriptive data about the criminal
histories of suspected serial sexual offenders using data from both criminal
history records and forensic DNA testing of sexual assault kits (SAKs).

## Installation
The *SSACHR* package is only available from a *private* repository available on 
[GitHub](https://github.com/) at https://github.com/sjpierce/SSACHR. It will 
remain private until we are ready to release the code, which will likely
coincide with publication of the associated paper. After that, we will make it a
public repository.

### Install SSACHR with Pre-Requisite Packages
Parts of the *SSACHR* package rely on functions from the *piercer* package, 
which is not yet available from [CRAN](https://CRAN.R-project.org). Releasing 
*piercer* on CRAN is a long-term goal but the development version can be 
obtained from a public [GitHub](https://github.com/) repository at 
https://github.com/sjpierce/piercer. The following code will install *devtools*,
*piercer*, and *SSACHR*. We use the *install_github()* function from *devtools*
to install the other two packages directly from the Github repositories. 

```r
install.packages("devtools")
devtools::install_github("sjpierce/piercer")
devtools::install_github("sjpierce/SSACHR")
```

```{r, echo = FALSE, eval = FALSE}
install.packages("devtools")
devtools::install_github("sjpierce/piercer")
devtools::install_github("sjpierce/SSACHR")
```

## Obtaining Data Files
The data files required by this package were deposited into the National Archive 
of Criminal Justice Data (Campbell, 2019). Please visit the web page for that 
deposit at [NACJD](https://doi.org/10.3886/ICPSR37134.v1) to download the files. 

After you have downladed the data from NACJD, unzip all the SPSS data files
(*.sav) into the data subfolder associated with your local copy of this 
repository. That should allow you to reproduce the analyses by re-running our 
scripts. 

## Example
Text goes here. 

```{r example}
#library(SSAlvmm)
# Need to add example code
```

# References
Campbell, R. (2019). Serial sexual assaults: A longitudinal examination of 
offending patterns using DNA evidence, Detroit, Michigan, 2009 [Data files, 
codebooks, computer programs, and statistical output]. ICPSR37134-v1. Ann Arbor,
MI: Inter-university Consortium for Political and Social Research [distributor],
2019-02-28. Retrieved from: https://doi.org/10.3886/ICPSR37134.v1

# Funding Support
This R package and repository are based on research supported by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (01/01/2015–12/31/2018). Serial 
sexual assaults: A longitudinal examination of offending patterns using DNA 
evidence. [NIJ Award # 2014-NE-BX-0006, Awarded, $699,533]. Sponsor: National 
Institute of Justice. Location: Michigan State University, East Lansing, MI.  

# Disclaimer
This research was supported by a grant from the National Institute of Justice, 
United States (2014-NE-BX-0006). The opinions or points of view expressed in 
this documents (or any other document included in this R package and repository)
are solely those of the authors and do not reflect the official positions of any
participating organization or the U.S. Department of Justice. 

## Task List
* Improve this file. 
* Create a script to generate a data flow diagram. 
