---
title: \sffamily{\bfseries{\LARGE Criminal History Records Paper (R Citations)}}
geometry: "left=.5in,right=.5in,top=.75in,bottom=.75in"
author: "Steven J. Pierce"
output:
 pdf_document:
   latex_engine: xelatex
   number_sections: true
   toc: yes
   toc_depth: 3
   includes:
     in_header: "compact-title.tex"
params: 
 LogFile: "R_Citations.pdf"
urlcolor: blue
header-includes:
- \usepackage{fancyhdr}
- \usepackage[yyyymmdd,hhmmss]{datetime}
- \usepackage{lastpage}
- \usepackage{fontspec}
- \defaultfontfeatures{Ligatures=TeX}
- \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
- \usepackage{url}
- \usepackage{floatrow}
- \floatplacement{figure}{!ht}
- \floatplacement{table}{!ht}
- \usepackage{placeins}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{dcolumn}
- \usepackage{titling}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}}
- \pagestyle{fancy}
- \lhead{SSA CHR Paper R Citations}
- \rhead{\today\ \currenttime}
- \lfoot{\texttt{\small \detokenize{`r params$LogFile`}}} 
- \cfoot{ }
- \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0.4pt}
- \renewcommand{\footrulewidth}{0.4pt}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

********************************************************************************  
\FloatBarrier

# Purpose.
This file just produces a list of R and R package citations so that we can give 
appropriate credit to the many people who developed or contributed to the 
software we relied on in doing this work. It's a separate file so that we can 
reduce redundancy across other PDF files produced by the various scripts. 

Version numbers in citations will be consistent with those used in other scripts 
if you knit this document from the same computer used for knitting those other 
scripts. Do that immediately after knitting all the other scripts. 

\FloatBarrier

# Setup
Set global R chunk options (local chunk options will over-ride global options). 
The method for creating a size option that controls font size in code chunks and
their text output is based on an answer to a question posted on   
[stackoverflow.com](https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex/46526740#46526740). 

``` {r global_options, cfsize = "footnotesize"}
# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", paste0("\n \\", options$cfsize,"\n\n", 
                                              x, "\n\n \\normalsize"), x)
  })

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE, cfsize = "footnotesize")

# Declare location of this script relative to the project root directory.
here::i_am(path = "inst/R_Citations.Rmd")
```

Load R packages that we need to get additional functions. 

``` {r load_packages}
library(here)             # for here()
library(rmarkdown)        # for render()
library(SSACHR)           # for git_report(), which_latex()
```

\FloatBarrier

# Project Information
These materials are scholarly products based on research funded by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (2015–2018). 
*Serial sexual assaults: A longitudinal examination of offending patterns using DNA evidence*. 
(NIJ Award # 2014-NE-BX-0006) [Grant]. National Institute of Justice. 

\FloatBarrier

# Software Information
We use R Markdown to enhance reproducibility. Knitting the source R Markdown 
script *`r knitr:::current_input()`* generates this PDF file.

- We used [RStudio](www.rstudio.org) to work with R and R markdown files. The 
  software chain looks like this: 
  **Rmd file > RStudio > R > rmarkdown > knitr > md file > pandoc > tex file > TinyTeX > PDF file**.
- We recommend using [TinyTeX](https://yihui.org/tinytex/) to compile LaTeX files 
  into PDF files. However, it should be viable to use 
  [MiKTeX](https://miktex.org) or another LaTeX distribution instead. 
- We used [pandoc](https://pandoc.org) `r pandoc_version()` for this 
  document. 

This document was generated using the following computational environment and 
dependencies: 

``` {r show_citations}
# Check and report whether we used TinyTex or other LaTeX software. 
which_latex()

# RStudio citation.
rstudioapi::versionInfo()

# Get R citation.
citation() 

# Get package citations.
citation("assertthat")
citation("car")
citation("descr")
citation("devtools")
citation("dplyr")
citation("emmeans")
citation("geepack")
citation("git2r")
citation("ggdist")
citation("ggplot2")
citation("haven")
citation("here")
citation("kableExtra")
citation("knitr")
citation("lattice")
citation("latticeExtra")
citation("lubridate")
citation("plyr")
citation("psych")
citation("rmarkdown")
citation("RColorBrewer")
citation("sjlabelled")
citation("SSACHR")
citation("texreg")
citation("tinytex")
citation("tidyr")
citation("utils")
citation("vistime")
```

The current Git commit details and status are:

```{r git_details, echo = TRUE, eval=TRUE}
git_report()
```
