---
title: \sffamily{\bfseries{\LARGE Criminal History Records Paper Step 1 (Data Management)}}
geometry: "left=.5in,right=.5in,top=.75in,bottom=.75in"
author: "Steven J. Pierce"
output:
 pdf_document:
   latex_engine: xelatex
   number_sections: true
   toc: yes
   toc_depth: 3
   includes:
     in_header: "compact-title.tex"
urlcolor: blue
header-includes:
- \usepackage{fancyhdr}
- \usepackage[yyyymmdd,hhmmss]{datetime}
- \usepackage{lastpage}
- \usepackage{fontspec}
- \defaultfontfeatures{Ligatures=TeX}
- \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
- \usepackage{url}
- \usepackage{floatrow}
- \floatplacement{figure}{!ht}
- \floatplacement{table}{!ht}
- \usepackage{placeins}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{dcolumn}
- \usepackage{titling}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}}
- \pagestyle{fancy}
- \lhead{SSA CHR Paper Step 1 Data Mgt}
- \rhead{\today\ \currenttime}
- \lfoot{\texttt{\small \detokenize{`r sub(".Rmd", ".pdf", knitr:::current_input(dir = FALSE))`}}} 
- \cfoot{ }
- \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0.4pt}
- \renewcommand{\footrulewidth}{0.4pt}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

********************************************************************************  
\FloatBarrier

# Purpose
This file imports copies of publicly archived data files (Campbell, 2019) into 
R, then performs data management to prepare a new data file for a descriptive 
paper about the criminal histories of suspected serial sexual perpetrators 
^[In this document, we use the terms perpetrator and offender interchangeably. 
Both terms should be interpreted as referring to individuals suspected of 
committing a crime but we occasionally omit that qualifier for the sake of 
brevity.]. The data come from Detroit, MI. 

Part of the analysis will require splitting each offender's criminal history 
into three periods: 

* Before the offender's earliest known sexual assault kit (SAK). 
* During a *testing window* that starts on the date of the offender's earliest 
  known SAK. This window operationalizes the concept of timely forensic testing. 
* After the end of the testing window. 

# Defining Timely Testing
One purpose of forensic testing for SAKs is to prevent future crimes by 
facilitating identification and arrest of suspected offenders. However, forensic
testing takes time to yield results. There are several steps that occur between 
SAK collection and law enforcement personnel being able to act on test results. 

There are examples of testing taking as little as a week for cases deemed to be
emergencies, but for non-emergency cases the testing time in Detroit had 
historically been much longer (typically 6-9 months, but 12-24 months was not 
uncommon) according to local stakeholders. 

Michigan's [2014 Sexual Assault Kit Evidence Submission Act (PA227)](http://www.legislature.mi.gov/(S(hsasgpdffxp4tsy3f3hpbxeo))/documents/mcl/pdf/mcl-Act-227-of-2014.pdf)
provides a working definition of timely testing by stipulating the following
requirements.

* Law enforcement agencies must take possession of an SAK within 14 days of 
  receiving notice from a health care facility that it has been collected. 
* Law enforcement agencies must submit the SAK to a lab for testing within 14 
  days of taking possession of it. 
* Laboratories must complete testing within 90 days after receiving an SAK. 

Adhering to those requirements would mean that law enforcement agencies should
be able to start acting on forensic results no later than 118 days after SAK
collection. Although some practitioners have reservations about the feasibility
of meeting the timing requirements in this law, it is nevertheless the best
working definition of timely testing available because it represents the outcome
of a public policy process in which multiple stakeholders had a voice.

In this study, we adopted an operational definition for the testing window based
on PA227's timing requirements. We defined the testing window as the first 118
days following the earliest SAK date associated with a suspected offender. It is
unrealistic to expect that crimes committed during this period could be
prevented by timely SAK testing because law enforcement personnel cannot act on
information they don’t have yet. Adopting a testing window definition based on 
the maximum duration consistent with the notion of timely testing is useful for
initial descriptive analyses that aim to characterize what crimes might have 
been prevented if timely testing had been done on the SAKs in this sample. 

\FloatBarrier

# Glossary

Here we define a few terms mentioned in this file. 

* **Data frame.** This is a just a tabular data set comprised of rows 
  (observations or cases) and columns (variables). 
* **Tibble.** The tidyverse group of R packages create and use a modified type 
  of data frame called tibbles. A tibble is still a tabular data set comprised 
  of rows (observations or cases) and columns (variables). 

# Setup
Set global R chunk options (local chunk options will over-ride global options). 
The method for creating a size option that controls font size in code chunks and
their text output is based on an answer to a question posted on   
[stackoverflow.com](https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex/46526740#46526740). 

``` {r global_options, cfsize = "footnotesize"}
# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", paste0("\n \\", options$cfsize,"\n\n", 
                                              x, "\n\n \\normalsize"), x)
  })

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE, cfsize = "footnotesize")

# Declare location of this script relative to the project root directory.
here::i_am(path = "inst/Step_01_Data_Mgt.Rmd")
```

Load R packages that we need to get additional functions. 

``` {r load_packages}
library(here)             # for here()
library(plyr)             # For mapvalues()
library(dplyr)            # for %>%, filter(), group_by(), & summarise()
library(tidyr)            # for arrange(), filter(), group_by(), mutate(),  
                          # spread(), summarise(), %>%, etc. 
library(rmarkdown)        # for render()
library(knitr)            # for kable()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)       # for kable_styling(), add_header_above(), column_spec(),
                          # collapse_rows(), and landscape()
library(descr)            # For freq().
options(descr.plot=FALSE) # Make freq() & crosstab() skip plots by default.
library(lubridate)        # For date conversion, eg. ymd(), time_length().
library(sjlabelled)       # For set_label(), get_label()
library(haven)            # for read_spss()
library(lattice)          # For xyplot(), bwplot(), etc. 
library(psych)            # For describe()
library(car)              # For recode()
library(SSACHR)           # for rvlabel()
```

\FloatBarrier

# Import Files
The SPSS files we will need to import, plus documentation about their contents
and relationships between them, are available from an online archive (Campbell,
2019). After you have a local copy of this SSACHR git repository on your 
computer, place the downloaded data files in the subfolder *SSACHR/inst/extdata* 
without changing the file names to minimize the effort involved in using this
script. Otherwise, you will need to update the file name references in the code
below. 

\FloatBarrier

## Core Criminal History Records (CHR) Files
Import the SPSS data files for the five core types of records comprising
Michigan criminal history records (CHR): offenders (IDN), incidents (INC),
arrest offenses (ARR), prosecutor charges (CHG), and judicial charges (JUD). 
See Campbell (2019) for details on these files. 

The variables we are updating with *rvlabel()* all have user-missing values with
labels that contain parentheses that are problematic when supplied to the 
*user.missing* argument in *freq()*, so we just remove the parentheses from the 
labels at import.

For the *ARR*, *CHG*, and *JUD* data, we use *dcode()* to convert the
categorical variables *ACat12*, *CCat12*, and *JCat12* into a set of dummy-code
variables with suffixes of the form *_x* where *x* includes the values 1-12 and
999. We also compute an new dummy code variable with the suffix *_Any* to code
records where the relevant crime category was any of the 12 main codes treated
as valid values instead of the user-missing code 999. These additional variables
facilitate later record selection and aggregation operations.

```{r import_IDN}
read_sav(here::here("inst/extdata/SSA_IDN_Offenders_2018-09-03.sav"), 
         user_na = TRUE) %>% 
  # Set variable label to match other core CHR files.
  var_labels(OID = "Offender ID (de-identified)") -> 
  IDN

# Make attributes for OID match those in other core CHR files.
attr(IDN$OID, "format.spss") <- "A4"
```

```{r import_INC}
read_sav(here::here("inst/extdata/SSA_INC_Incidents_Imputed_2018-09-03.sav"), 
         user_na = TRUE) ->
  INC
```

```{r import_ARR}
read_sav(here::here("inst/extdata/SSA_ARR_Arrests_Imputed_2018-09-03.sav"), 
         user_na = TRUE) %>% 
  # Replace user-missing value labels.
  mutate(ACat12 = rvlabel(ACat12),
         ACat10 = rvlabel(ACat10),
         ACat04 = rvlabel(ACat04)) %>% 
  # Dummy code crime category variables. 
  dcode(x = ., y = factor(.$ACat12), stem = "ACat12") %>% 
  # Dummy code any of the 12 main crime categories, set user-missing values to 0. 
  mutate(ACat12_Any = if_else(ACat12 %in% 1:12, true = 1, false = 0)) %>% 
  var_labels(ACat12_1   = "Arrested for arson",
             ACat12_2   = "Arrested for assault - DV, stalking",
             ACat12_3   = "Arrested for assault - non-sexual, non-DV",
             ACat12_4   = "Arrested for burglary",
             ACat12_5   = "Arrested for criminal sexual conduct",
             ACat12_6   = "Arrested for drug crime",
             ACat12_7   = "Arrested for homicide",
             ACat12_8   = "Arrested for larceny/theft/fraud",
             ACat12_9   = "Arrested for robbery", 
             ACat12_10  = "Arrested for sex crime, other excluding CSC",
             ACat12_11  = "Arrested for traffic/ordinances",
             ACat12_12  = "Arrested for weapons",
             ACat12_999 = "Arrested for excluded user-missing",
             ACat12_Any = "Arrested for any of 12 main crime categories") ->
  ARR
```

```{r import_CHG}
read_sav(here::here("inst/extdata/SSA_CHG_PA_Charges_Imputed_2018-09-03.sav"), 
         user_na = TRUE) %>% 
  # Replace user-missing value labels.
  mutate(CCat12 = rvlabel(CCat12),
         CCat10 = rvlabel(CCat10),
         CCat04 = rvlabel(CCat04)) %>% 
  # Dummy code crime category variables. 
  dcode(x = ., y = factor(.$CCat12), stem = "CCat12") %>% 
  # Dummy code any of the 12 main crime categories, set user-missing values to 0. 
  mutate(CCat12_Any = if_else(CCat12 %in% 1:12, true = 1, false = 0)) %>% 
  var_labels(CCat12_1   = "Charged for arson",
             CCat12_2   = "Charged for assault - DV, stalking",
             CCat12_3   = "Charged for assault - non-sexual, non-DV",
             CCat12_4   = "Charged for burglary",
             CCat12_5   = "Charged for criminal sexual conduct",
             CCat12_6   = "Charged for drug crime",
             CCat12_7   = "Charged for homicide",
             CCat12_8   = "Charged for larceny/theft/fraud",
             CCat12_9   = "Charged for robbery", 
             CCat12_10  = "Charged for sex crime, other excluding CSC",
             CCat12_11  = "Charged for traffic/ordinances",
             CCat12_12  = "Charged for weapons",
             CCat12_999 = "Charged for excluded user-missing",
             CCat12_Any = "Charged for any of 12 main crime categories") ->
  CHG
```

```{r import_JUD}
read_sav(here::here("inst/extdata/SSA_JUD_Judicial_Charges_Imputed_2018-09-03.sav"), 
         user_na = TRUE) %>% 
  # Replace user-missing value labels.
  mutate(JCat12 = rvlabel(JCat12),
         JCat10 = rvlabel(JCat10),
         JCat04 = rvlabel(JCat04)) %>% 
  # Dummy code crime category variables. 
  dcode(x = ., y = factor(.$JCat12), stem = "JCat12") %>% 
  # Dummy code any of the 12 main crime categories, set user-missing values to 0. 
  mutate(JCat12_Any = if_else(JCat12 %in% 1:12, true = 1, false = 0)) %>% 
  var_labels(JCat12_1   = "Adjudicated for arson",
             JCat12_2   = "Adjudicated for assault - DV, stalking",
             JCat12_3   = "Adjudicated for assault - non-sexual, non-DV",
             JCat12_4   = "Adjudicated for burglary",
             JCat12_5   = "Adjudicated for criminal sexual conduct",
             JCat12_6   = "Adjudicated for drug crime",
             JCat12_7   = "Adjudicated for homicide",
             JCat12_8   = "Adjudicated for larceny/theft/fraud",
             JCat12_9   = "Adjudicated for robbery", 
             JCat12_10  = "Adjudicated for sex crime, other excluding CSC",
             JCat12_11  = "Adjudicated for traffic/ordinances",
             JCat12_12  = "Adjudicated for weapons",
             JCat12_999 = "Adjudicated for excluded user-missing",
             JCat12_Any = "Adjudicated for any of 12 main crime categories") ->
  JUD
```

\FloatBarrier

## SAK-Perpetrator Data File
We need this additional data file to identify the earliest SAK associated with
each offender. See Campbell (2019) for details on this file.  

``` {r import_SPD}
# Read SPSS data file.
read_sav(here::here("inst/extdata/SAK_PERP_2018-04-03.sav"), 
         user_na = TRUE) %>% 
  # Sort by OID and SAK collection date (but NAs are last in sort order).
  arrange(OID, SDate.Yr, SDate.Mt, SDate) %>% 
  # Add a variable showing how many unique SAKs the offender has.
  add_count(OID, name = "OID_NSAK") %>% 
  # Make a OID variable label match the lbel used in CHR data sets. 
  var_labels(OID = "Offender ID (de-identified)",
             OID_NSAK = "No. of unique SAKs associated with this offender") ->
  SPD
```

\FloatBarrier

# Data Management

\FloatBarrier

## Create Conviction Dataset
Convictions are the subset of adjudicated charges that have a specific 
disposition code indicating that the offender was convicted. For simplicity, we 
extract them to a new tibble. Note that in this *CON* tibble, the *NCON* 
variable is marking all convictions, even those for crimes that fall into the
user-missing category *JCat12* = 999. 
 
```{r create_CON}
# Create a subset of JUD containing only charges where offender was convicted.
JUD %>% 
  # Retain a subset of JUD records based on disposition.
  filter(JDispCat == 1) %>% 
  # Add a variable to CON to simplify aggregation later. 
  mutate(NCON = 1) %>% 
  # Add variable label. 
  var_labels(JCat12_1   = "Convicted for arson",
             JCat12_2   = "Convicted for assault - DV, stalking",
             JCat12_3   = "Convicted for assault - non-sexual, non-DV",
             JCat12_4   = "Convicted for burglary",
             JCat12_5   = "Convicted for criminal sexual conduct",
             JCat12_6   = "Convicted for drug crime",
             JCat12_7   = "Convicted for homicide",
             JCat12_8   = "Convicted for larceny/theft/fraud",
             JCat12_9   = "Convicted for robbery", 
             JCat12_10  = "Convicted for sex crime, other excluding CSC",
             JCat12_11  = "Convicted for traffic/ordinances",
             JCat12_12  = "Convicted for weapons",
             JCat12_999 = "Convicted for excluded user-missing",
             JCat12_Any = "Convicted for any of 12 main crime categories",
             NCON       = "Adjudicated charge record w/ conviction") ->
  CON
```

\FloatBarrier

## Merge Number of Convictions onto IDN Dataset

```{r merge_CON_IDN}
# Merge NCON conviction charge count variable into IDN.
CON %>% 
  group_by(OID) %>% 
  summarize_at(.vars = "NCON", .funs = c("sum")) %>% 
  ungroup() %>% 
  left_join(x = IDN, y = ., by = "OID") %>% 
  # Recode NCON variable to replace NA with 0. 
  replace_na(data = ., replace = list(NCON = 0)) %>%  
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(IDN), "NCON"))) %>% 
  # Add variable labels. 
  var_labels(NCON = "No. of adjudicated charge records w/ convictions") -> 
  IDN
```

## Identify Earliest SAK for Each Offender
For the paper, we need to identify the earliest SAK associated with each 
offender who has criminal history data and store those in a new dataset. Along 
the way, we need to do several intermediate tasks. 

According to the help files, *dplyr::arrange* always puts NA values last in 
the sort order. That means we need to use a trick to adjust for that when we 
use that function to sort the data. 

First, we have to trim the SPD data down to just the SAKs associated with 
offenders for whom we have criminal history data (SPDCHR). 

```{r create_SPDCHR}
SPD %>% 
  # Retain only offenders with CHR data. 
  filter(OIDinCHR == "Yes") -> 
  SPDCHR 
```

With the resulting *SPDCHR* data, we need to identify the start of the testing
window for each SAK and store it in a new variable called *WDate*, then
aggregate across SAKs associated with each offender to identify the earliest
*WDate* value. 

\FloatBarrier

### Identify Start of Testing Window for each SAK
The testing window for a SAK should start on the date it was collected. We
already have a variable called *SDate* that records this information. However, 
some SAKs have only partial date information, leaving *SDate* with NA values. A
very small number of SAKs have completely missing data on *SDate* such that not
even the year of collection is known, but most of the cases with missing *SDate*
values have the year of collection recorded in *SDate.Yr* and some also have the
month recorded in *SDate.Mt*.

SAK collection dates (*SDate*) were recorded by hospitals (or other healthcare
providers) who actually collected the SAKs. These dates are very likely to be
accurate because healthcare providers have a strong financial incentive to get
dates of service correct for billing purposes. 

However, when we have missing or partial *SDate* data, we have an additional
source of data that might provide an exact date for the start of the testing
window (*WDate*). In our prior work with these data, we linked some SAKs to
existing CHR incident records that involved criminal sexual conduct (as
evidenced by an associated arrest offense record, prosecutor charge record, or
judicial charge record for a sexual assault). Those links were created to
recognize possible overlap between sexual assaults represented in the CODIS hits
(CHITS) data from the SAK testing and the CHR data files. We did not require
exact date matches in the previous work because we were dealing with data that
originated from different organizations. We allowed up to a 45 day discrepancy
in the dates when making matches.

For SAKs that are not linked to an incident record, *OID_IID* = "" (an empty 
string) and *OID_IDate* = NA. Therefore, the only date information available is
in the SAK collection date variables (*SDate*, *SDate.Yr*, and *SDate.Mt*). If
we have a valid value in *SDate*, then *WDate* = *SDate*. When we only have
partial date information, then *SDate* is missing but *SDate.Yr* and possibly
also *SDate.Mt* have valid values, but we cannot assign a precise date to the
SAK collection and *WDate* ends up with a missing value.

For SAKs that were linked to an incident record, *OID_IID* stores the incident
ID value that links to the CHR incident record in the *INC* data and *OID_IDate*
stores the corresponding incident date. Thus, if *SDate* is missing, we set
*WDate* = *OID_IDate* instead, thereby using *OID_IDate* as supplementary 
information to reduce missing data in *WDate*. 

We also create a *TWindow* date interval variable to record the start and end 
dates for the 118-day testing window for each of these SAKs. 

```{r create_SPDCHRE}
SPDCHR %>% 
  mutate(# Testing Window Start Date.
         WDate = case_when(
           # Default to using SDate if it is not missing. 
           is.na(SDate) == FALSE ~ SDate,
           # If SDate is incomplete or missing, use a valid OID_IDate instead. 
           is.na(SDate) == TRUE & is.na(OID_IDate) == FALSE ~ OID_IDate),
         # Testing Window Start Year.
         WDate.Yr = case_when(
           # Default to year of WDate if it is not missing.
           is.na(WDate) == FALSE ~ year(WDate),
           # Otherwise use SDate.Yr
           is.na(WDate) == TRUE ~ SDate.Yr),
         # Testing Window Start Month.
         WDate.Mt = case_when(
           is.na(WDate) == FALSE ~ month(WDate),
           is.na(WDate) == TRUE ~ SDate.Mt),
         # Testing Window Start Date Status.
         WDate.Status = case_when(
           is.na(WDate) == TRUE & is.na(WDate.Yr) == TRUE ~ "Missing",
           is.na(WDate) == TRUE & is.na(WDate.Mt) == TRUE ~ "Partial.Y",
           is.na(WDate) == TRUE & is.na(WDate.Mt) == FALSE ~ "Partial.YM",
           is.na(WDate) == FALSE ~ "Known"),
         # Testing Window Date Interval.
         TWindow = interval(WDate, WDate + 118)) %>% 
  # Sort records by year, month, and date but ensure that within each layer 
  # records with missing data come first. 
  arrange(OID, -is.na(WDate.Yr), WDate.Yr, -is.na(WDate.Mt), WDate.Mt, WDate) %>% 
  # Group by OID, then select first record for each offender. 
  group_by(OID) %>% 
  filter(row_number() == 1) %>% 
  # Ungroup to ensure simpler, more predictable tibble behavior later. 
  ungroup() %>% 
  # Add variable labels. 
  var_labels(WDate = "Testing Window Start Date",
             WDate.Yr = "Testing Window Start Year",
             WDate.Mt = "Testing Window Start Month",
             WDate.Status = "Testing Window Start Date Status",
             TWindow = "Testing Window Date Interval") ->
  SPDCHRE
```

The code above takes the *SPDCHR* dataset, adds new variables pertaining to 
the start of the testing window, sorts the data into chronological order, then 
drops everything but the earliest SAK for each perpetrator. The result is saved
to the *SPDCHRE* dataset

\FloatBarrier

### Missingness Status for Earliest SAK Testing Window Start Date
Here we pause to assess how many of the offenders with CHR data have missing 
*WDate* values for their earliest SAK. Table \ref{tab:examine_WDate} shows 
a cross-tabulation of the number of SAKs associated with a perpetrator 
(*OID_NSAK*) against the status of the *WDate* variable. 

```{r examine_WDate}
# Table caption.
TCap <- paste("Number of SAKs by WDate Status for Perpetrator's Earliest SAK")
# Footnote text.
FN <- paste("Cells contain counts of perpetrators. Only perpetrators for whom",
            "criminal history records are available were included.",
            "No. SAKs, total number of SAKs associated with perpetrator;",
            "WDate, start date for testing window;",
            "Y, M, and D, respectively refer to the year, month, and day", 
            "components of WDate. Letters replaced by question marks (?)",
            "show which components are unknown.")

# Vector of text values for column labels to be used in the table.
clabels <- c("No. SAKs", "YMD", "YM?", "Y??", "???", "Sum")

addmargins(xtabs(~OID_NSAK + WDate.Status, addNA = TRUE, data = SPDCHRE)) %>% 
  as.data.frame() %>% 
  pivot_wider(names_from = WDate.Status, values_from = Freq) %>% 
  select(OID_NSAK, Known, Partial.YM, Partial.Y, Missing, Sum) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, 
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  add_header_above(c("", "Known", "Partial" = 2, "Missing", "")) %>% 
  add_header_above(c("", "WDate Status" = 4, "")) %>% 
  column_spec(1, width = "1.8cm") %>% 
  column_spec(2:6, width = "1.2cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

```{r create_SPDCHREW}
SPDCHRE %>% 
  # Retain only the earliest SAKs with known WDate values. 
  filter(WDate.Status == "Known") %>% 
  # Rename variables for clarity. 
  dplyr::rename(ESAKID = SAKID, 
                ESAK_IID = OID_IID) %>% 
  # Add variable labels.
  var_labels(ESAKID = "SAK ID for Offender's Earliest SAK",
             ESAK_IID = "Incident ID for Offender's Earliest SAK",
             TWindow = "Testing Window Date Interval") ->
  SPDCHREW
```

We have complete, known *WDate* values for `r nrow(SPDCHREW)` 
(`r round(100*nrow(SPDCHREW)/nrow(SPDCHRE))`%) of the `r nrow(SPDCHRE)`
perpetrators with CHR data. That leaves `r nrow(SPDCHRE) - nrow(SPDCHREW)`
perpetrators with missing or partial information for *WDate*. For perpetrators 
completely missing values on one or more of their SAKs, it is impossible to tell
which was the earliest SAK. There is no way we can split their criminal 
histories into the three periods for before, during, and after the testing
window. 

We know only the year of earliest SAK collection for most of the perpetrators
with partial *WDate* information. We have not identified a reasonable and
defensible method for imputing precise *WDate* values for these offenders.
Therefore, we have excluded them from the sample analyzed for this paper by
trimming the *SPDCHRE* dataset down to just those offenders who have a known
*WDate* and saving the results as the *SPDCHREW* dataset. This is an 
offender-level dataset. 

\FloatBarrier

## Merge Testing Window Variables Onto IDN Data
Merging the testing window variables onto the *IDN* data is an obvious next
step. Then we subset down to the records that have non-missing *WDate* values
and select only the variables we need to keep before setting a variable label
and saving to a new tibble called *IDNEW*.

After merging in *TWindow*, it is now possible to compute date intervals for 
the periods of the recorded criminal history observed before and after the 
testing window. We call those new variables *BWindow* and *AWindow* and 
supplement all three date intervals with duration variables measuring the 
duration of the before, during, and after periods in years (*DurationBP*, 
*DurationDP*, and *DurationAP*, respectively). We will eventually use these 
duration variables as offsets when modeling count outcome variables that need to
adjust for period duration to produce crime incidence rate variables.

We are working with adult criminal history records that only include data for
crimes committed since each offender reached 16 years of age. Therefore, the
offender's 16th birth day (*Age16Date*) is the obvious start date for the before
period. However, because *WDate* is derived from when the earliest
SAK for the offender was collected rather than the criminal history data,
*WDate* can in principle either precede or occur on *Age16Date* (which can be 
computed from from date of birth *DOB*). We create variables below that help us 
determine how often that occurred and adjust the before period date interval in
a sensible way when it does. 

We defined the before period as starting on the offender's 16th birthday 
(*Age16Date*) and ending one day before the earliest SAK was collected (*WDate*)
when *Age16Date* < *WDate*, and otherwise as both starting and ending the day 
before *WDate*. That yields a before period with a positive duration for most 
offenders but zero years for those whose earliest SAK was collected before they 
reached age 16 years. 

For all offenders, the after period starts on the 119th day after *WDate*
(because the testing window is 118 days long) and ends on the data collection
date when the criminal history data were extracted from the state data
warehouse: April 15, 2016. 


**Insert a figure here** to illustrate computation of the durations of the 
before, during, and after periods. Use the SSACHR_Period_Durations.xlsx as 
a guide, implement the figure with [vistime package](https://cran.r-project.org/web/packages/vistime/vignettes/vistime-vignette.html)

```{r plot_periods}
# Plot a figure showing how we compute observed period durations.
```


```{r create_IDNEW}
SPDCHREW %>% 
  # Retain only variables we need to merge into IDN.
  select(ESAKID, OID, ESAK_IID, WDate, TWindow) %>% 
  # Merge SPDCHREW variables onto INC rows. 
  right_join(x = ., y = IDN, by = "OID") %>% 
  # Retain only IDN records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>%
  # Create more variables.
  mutate(
    # Offender 16th birthday (start of before period).
    Age16Date = DOB + dyears(16),
    # Offender age at start of earliest SAK testing window
    AgeWDate = interval(DOB, WDate)/dyears(1),
    # Did offender turn 16 before WDate (start of testing window, TWindow)?
    Turn16_Before_WDate = (Age16Date < WDate),
    # Did offender turn 16 on or after WDate (start of testing window, TWindow)?
    Turn16_After_WDate = (Age16Date >= WDate),
    # Data Collection Date (end of after period)
    DCDate = ymd("2016-04-15", tz = "UTC"),  
    # Did testing window end before data collection date?
    End_TWindow_Before_DC = (WDate + 118 < DCDate),
    # Observed window date interval
    OWindow = interval(Age16Date, DCDate),
    # Before testing window date interval
    BWindow = case_when(
      # If offender turned 16 before WDate, before period lasts > 0 years.
      Turn16_Before_WDate ~ interval(Age16Date, WDate - 1),
      # If offender turned 16 on or after WDate, before period lasts 0 years.
      Turn16_After_WDate ~ interval(WDate - 1, WDate - 1)),
    # After testing window date interval. 
    AWindow = interval(WDate + 119, DCDate),
    # Duration of before testing window period (years).
    DurationBP = case_when(
      Age16Date <  WDate - 1 ~ (as.duration(BWindow) + ddays(1))/dyears(1),
      Age16Date == WDate - 1 ~ ddays(1)/dyears(1),
      Age16Date >  WDate - 1 ~ 0),
    # Duration of during testing window period (years)
    DurationDP = case_when(
      Age16Date < WDate ~ ddays(119)/dyears(1),
      Age16Date %within% TWindow ~ 
        (as.duration(intersect(OWindow, TWindow)) + ddays(1))/dyears(1),
      Age16Date > WDate + 118 ~ 0),
    # Duration of after testing window period (years)
    DurationAP = case_when(
      Age16Date <= WDate + 119 ~ (as.duration(AWindow) + ddays(1))/dyears(1),
      Age16Date >  WDate + 119 ~ 
        (as.duration(intersect(OWindow, AWindow)) + ddays(1))/dyears(1))) %>% 
  var_labels(
    Age16Date = "Offender 16th Birthday",
    AgeWDate = "Offender Age at Start of Earliest SAK Testing Window (Years)",
    Turn16_Before_WDate = "Offender Turned 16 Before Start of Testing Window",
    Turn16_After_WDate = "Offender Turned 16 On or After Start of Testing Window",
    DCDate = "Data Collection Date for Criminal history Records",
    End_TWindow_Before_DC = "Testing Window Ended Before Data Collection Date",
    DurationBP = "Duration of before testing window period (years)",
    DurationDP = "Duration of during testing window period (years)",
    DurationAP = "Duration of after testing window period (years)",
    BWindow = "Before Testing Window Date Interval",
    TWindow = "Testing Window Date Interval",
    AWindow = "After Testing Window Date Interval") %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(IDN), "Age16Date", "ESAKID", "ESAK_IID", "WDate", 
                  "TWindow", "Turn16_Before_WDate", "Turn16_After_WDate", 
                  "DCDate", "End_TWindow_Before_DC", "BWindow", "AWindow", 
                  "DurationBP", "DurationDP", "DurationAP"))) ->
  IDNEW
```

We end up with an *IDNEW* tibble that has `r nrow(IDNEW)` of the original 
`r nrow(IDN)` perpetrators with CHR data. Only `r sum(IDNEW$Turn16_After_WDate)`
of the `r nrow(IDNEW)` offenders turned 16 on or after their earliest SAK was 
collected and the testing window had started; they therefore have *DurationBP* 
= 0 years. 

## Merge Testing Window Variables Onto Incident Data
The next step is to merge variables from *IDNEW* onto the incident data in *INC*
so that we can classify each incident according to whether it occurred before,
during, or after the earliest testing window for the offender in the new *IWhen*
variable. Along the way we rename some variables and update variable labels for
clarity. Then we select only the variables we need to keep and subset down to
the records that have non-missing *WDate* values and save to a new tibble called
*INCEW*. 

The *INCEW* tibble still contains one record for every incident associated with
the offenders contained in *IDNEW*, regardless of what crime categories were
associated with the incident. This will change later in the script, after we 
construct and merge in additional variables that make it easy to subset *INCEW*
to records for incidents associated with at least one arrest, charge, or 
conviction for one of the 12 main crime categories of interest. 

```{r create_INCEW}
# Object to hold names of IWhen levels.
IWhenLevels <- c("Before", "During", "After")

# Object to hold names of crucial testing window variables
twvars <- c("ESAKID", "ESAK_IID", "WDate", "TWindow", "IWhen")

# Data management for the merge. 
IDNEW %>% 
  # Retain only variables we need to merge into INC.
  select(ESAKID, OID, ESAK_IID, WDate, TWindow) %>% 
  # Merge IDNEW variables onto INC rows. 
  right_join(x = ., y = INC, by = "OID") %>% 
  # Retain only INC records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>% 
  # Add more variables. 
  mutate(# Classify incidents as before, during, or after the testing window. 
         IWhen = case_when(
           # If incident matched to earliest SAK, incident was in the window.
           ESAK_IID == IID ~ "During",
           # Otherwise, compare IDate to TWindow to determine if incident was in
           # the window. 
           IDate < int_start(TWindow) ~ "Before",
           IDate %within% TWindow ~ "During",
           IDate > int_end(TWindow) ~ "After")) %>% 
  # Convert IWhen to a factor with levels in sensible order for display.
  mutate(IWhen = factor(IWhen, levels = IWhenLevels, ordered = TRUE)) %>% 
  # Add variable labels.
  var_labels(IWhen = "When was incident relative to testing window?") %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(INC), twvars))) %>% 
  # Add another variable label that was otherwise being dropped. 
  var_labels(TWindow = "Testing Window Date Interval") ->
  INCEW
```

Table \ref{tab:examine_INCEW_IWhen} shows the frequency distribution for when 
the incidents occurred relative to the testing window. 

```{r examine_INCEW_IWhen}
# Table caption.
TCap <- paste("Frequency Distribution of When Incident Occurred Relative to",
              "Testing Window")
# Footnote text.
FN <- paste("Only incidents with valid testing window start dates were",
            "included. IWhen, when was incident relative to testing window?")

# Vector of text values for column labels to be used in the table.
clabels <- c("IWhen", "Frequency", "Percent")

xtabs(~IWhen, data = INCEW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(INCEW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

We used one special case decision rule when classifying incidents. If an 
incident record had been previously linked to the perpetrator's earliest SAK in
the SPD tibble, then the *IID* variable in the INC record will have a value 
matching the *ESAK_IID* variable merged in from the IDNEW tibble. Such
incidents must by definition be treated as occurring during the testing window
even if the *IDate* lies outside the window. This reflects the notion that we 
are trusting the *SDate* values more than *IDate* values when constructing
*WDate* and *TWindow*. Table \ref{tab:examine_IDate} shows that there are only a
few incidents matched to the perpetrator's earliest SAK where this decision rule
classifies an incident as occurring during the testing window even though
*IDate* actually falls outside that date interval. 

```{r examine_IDate}
# Table caption.
TCap <- paste("Crosstabulation of Whether Incident Date Was Within Testing",
              "Window and Whether Incident Matched to Perpetrator's Earliest",
              "SAK")
# Footnote text.
FN <- paste("Cells contain counts of incidents. Only incidents with valid",
            "testing window start dates were included. ESAK, earliest sexual",
            "assault kit; IDate, incident date; TWindow, testing window.")

# Vector of text values for column labels to be used in the table.
clabels <- c("IDate in TWindow", "FALSE", "TRUE", "Sum")

xtabs(~IDate %within% TWindow + (ESAK_IID == IID), addNA = TRUE, data = INCEW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  pivot_wider(names_from = ESAK_IID....IID, values_from = Freq) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, 
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  add_header_above(c("", "Matched to ESAK" = 2, "")) %>% 
  column_spec(1, width = "3cm") %>% 
  column_spec(2:4, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

Now, we need to get offender-level counts of incidents that occurred before,
during, and after the testing window respectively called *NINC_Before*,
*NINC_During*, and *NINC_After*. We can aggregate as follows to get them. We
also merge these variables into *IDNEW*. However, these incident count variables
are not restricted to incidents involving arrest, charge, or conviction for one
or more of the 12 main crime categories. We will construct additional variables
consistent with that criterion later.

```{r merge_Agg_NINC_IWhen_IDNEW}
INCEW %>% 
  mutate(NINC = 1) %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  # Aggregate by OID and IWhen to get count variables
  summarize(NINC = sum(NINC)) %>% 
  pivot_wider(names_from = IWhen, values_from = NINC, 
              names_glue = "NINC_{IWhen}") %>% 
  var_labels(NINC_Before = "No. of incident records before testing window",
             NINC_During = "No. of incident records during testing window",
             NINC_After  = "No. of incident records after testing window") %>% 
  # Merge incident record count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(c("NINC_Before", "NINC_During", "NINC_After")), 
                .fns = replace_na, replace = 0)) ->
  IDNEW
```
\FloatBarrier

## Merge Testing Window Variables Onto Arrest Records
The next step is to merge variables from *INCEW* onto the arrest data in *ARR*
so that we can classify each arrest offense record according to whether the
incident associated with it occurred before, during, or after the earliest
testing window for the offender by using *IWhen*. Then we subset down to the
*ARR* records that have non-missing *WDate* values plus *ACat12_Any* = 1, then
select only the variables we need to keep before saving a new tibble called
*ARREW*.

```{r create_ARREW}
INCEW %>% 
  # Retain only variables we need to merge into ARR.
  select(IID, ESAKID, ESAK_IID, WDate, TWindow, IWhen) %>% 
  # Merge INCEW variables onto ARR rows. 
  right_join(x = ., y = ARR, by = "IID") %>% 
  # Retain only ARR records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>% 
  # Retain only ARR records for the main 12 crime categories, dropping 999.
  filter(ACat12_Any == 1) %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(ARR), twvars))) %>% 
  # Add a variable label that was otherwise being dropped. 
  var_labels(TWindow = "Testing Window Date Interval") ->
  ARREW 
```

The original *ARR* tibble had `r nrow(ARR)` arrest offense records. Dropping the
records associated with offenders whose earliest testing window could not be
identified or that were coded *ACat12_Any* = 0 because *ACat12* = 999 (excluded 
user-missing) leaves `r nrow(ARREW)` arrest offense records in *ARREW*. Table 
\ref{tab:examine_ARREW_IWhen} shows how many arrest offense records were 
associated with incidents that occurred before, during, and after the testing 
window. 

```{r examine_ARREW_IWhen}
# Table caption.
TCap <- paste("Frequency Distribution of When the Incident Associated With An",
              "Arrest Offense Record Occurred Relative to Testing Window")
# Footnote text.
FN <- paste("Only arrest offense records for incidents with valid testing",
            "window start dates and offenses from the 12 crime categories",
            "of interest were included. IWhen, when was incident relative to", 
            "testing window?")

# Vector of text values for column labels to be used in the table.
clabels <- c("IWhen", "Frequency", "Percent")

xtabs(~IWhen, data = ARREW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(ARREW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

Now, we need to get offender-level counts of arrest offense records associated 
with incidents that occurred before, during, and after the testing window 
respectively called *NARR12_Before*, *NARR12_During*, and *NARR12_After*. We can 
aggregate as follows to get them. We merge these variables into *IDNEW* too. 
These new aggregated variables respect the criterion of counting only offenses 
in the 12 main crime categories of interest because of the case selection that
went into building the *ARREW* data. 

```{r merge_Agg_NARR_IWhen_IDNEW}
ARREW %>% 
  mutate(NARR12 = 1) %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  # Aggregate by OID and IWhen to get count variables
  summarize(NARR12 = sum(NARR12)) %>% 
  pivot_wider(names_from = IWhen, values_from = NARR12, 
              names_glue = "NARR12_{IWhen}") %>% 
  var_labels(NARR12_Before = "No. of arrest offense records from 12 main crime categories before testing window",
             NARR12_During = "No. of arrest offense records from 12 main crime categories during testing window",
             NARR12_After  = "No. of arrest offense records from 12 main crime categories after testing window")  %>% 
  # Merge arrest offense record count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(c("NARR12_Before", "NARR12_During", "NARR12_After")), 
                .fns = replace_na, replace = 0)) %>% 
  # Compute alternate NARR for records from 12 main crime categories. 
  mutate(NARR12 = NARR12_Before + NARR12_During + NARR12_After) %>% 
  var_labels(NARR12 = "No. of arrest offense records from 12 main crime categories") ->
  IDNEW
```

\FloatBarrier

## Merge Testing Window Variables Onto Prosecutor Charge Records
The next step is to merge variables from *INCEW* onto the charge data in *CHG*
so that we can classify each prosecutor charge record according to whether the
incident associated with it occurred before, during, or after the earliest
testing window for the offender by using *IWhen*. Then we subset down to the
*CHG* records that have non-missing *WDate* values plus *CCat12_Any* = 1, then
select only the variables we need to keep before saving a new tibble called 
*CHGEW*.

```{r create_CHGEW}
INCEW %>% 
  # Retain only variables we need to merge into CHG.
  select(IID, ESAKID, ESAK_IID, WDate, TWindow, IWhen) %>% 
  # Merge INCEW variables onto CHG rows. 
  right_join(x = ., y = CHG, by = "IID") %>% 
  # Retain only CHG records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>% 
  # Retain only CHG records for the main 12 crime categories, dropping 999.
  filter(CCat12_Any == 1) %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(CHG), twvars))) %>% 
  # Add a variable label that was otherwise being dropped. 
  var_labels(TWindow = "Testing Window Date Interval") ->
  CHGEW 
```

The original *CHG* tibble had `r nrow(CHG)` prosecutor charge records. Dropping
the records associated with offenders whose earliest testing window could not be
identified or that were coded *CCat12_Any* = 0 because *CCat12* = 999 (excluded 
user-missing) leaves `r nrow(CHGEW)` prosecutor charge records in *CHGEW*. Table
\ref{tab:examine_CHGEW_IWhen} shows how many prosecutor charge records were
associated with incidents that occurred before, during, and after the testing
window.

```{r examine_CHGEW_IWhen}
# Table caption.
TCap <- paste("Frequency Distribution of When the Incident Associated With A",
              "Prosecutor Charge Record Occurred Relative to Testing Window")
# Footnote text.
FN <- paste("Only prosecutor charge records for incidents with valid testing",
            "window start dates and offenses from the 12 crime categories", 
            "of interest were included. IWhen, when was incident relative", 
            "to testing window?")

# Vector of text values for column labels to be used in the table.
clabels <- c("IWhen", "Frequency", "Percent")

xtabs(~IWhen, data = CHGEW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(CHGEW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

Now, we need to get offender-level counts of prosecutor charge records
associated with incidents that occurred before, during, and after the testing
window respectively called *NCHG12_Before*, *NCHG12_During*, and *NCHG12_After*. We
can aggregate as follows to get them. We merge these variables into *IDNEW* too.
These new aggregated variables respect the criterion of counting only offenses
in the 12 main crime categories of interest because of the case selection that
went into building the *CHGEW* data.


```{r merge_Agg_NCHG_IWhen_IDNEW}
CHGEW %>% 
  mutate(NCHG12 = 1) %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  # Aggregate by OID and IWhen to get count variables
  summarize(NCHG12 = sum(NCHG12)) %>% 
  pivot_wider(names_from = IWhen, values_from = NCHG12, 
              names_glue = "NCHG12_{IWhen}") %>% 
  var_labels(NCHG12_Before = "No. of prosecutor charge records from 12 main crime categories before testing window",
             NCHG12_During = "No. of prosecutor charge records from 12 main crime categories during testing window",
             NCHG12_After  = "No. of prosecutor charge records from 12 main crime categories after testing window") %>% 
  # Merge charge record count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(c("NCHG12_Before", "NCHG12_During", "NCHG12_After")), 
                .fns = replace_na, replace = 0)) %>% 
  # Compute alternate NCHG for records from 12 main crime categories.
  mutate(NCHG12 = NCHG12_Before + NCHG12_During + NCHG12_After) %>% 
  var_labels(NCHG12 = "No of prosecutor charge records from 12 main crime categories") ->
  IDNEW
```

\FloatBarrier

## Merge Testing Window Variables Onto Judicial Charge Records
The next step is to merge variables from *INCEW* onto the charge data in *JUD*
so that we can classify each judicial charge record according to whether the
incident associated with it occurred before, during, or after the earliest
testing window for the offender by using *IWhen*. Then we subset down to the
*JUD* records that have non-missing *WDate* values plus *JCat12_Any* = 1, then 
select only the variables we need to keep before saving a new tibble called
*JUDEW*.

```{r create_JUDEW}
INCEW %>% 
  # Retain only variables we need to merge into JUD.
  select(IID, ESAKID, ESAK_IID, WDate, TWindow, IWhen) %>% 
  # Merge INCEW variables onto JUD rows. 
  right_join(x = ., y = JUD, by = "IID") %>% 
  # Retain only JUD records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>% 
  # Retain only JUD records for the main 12 crime categories, dropping 999.
  filter(JCat12_Any == 1) %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(JUD), twvars))) %>% 
  # Add a variable label that was otherwise being dropped. 
  var_labels(TWindow = "Testing Window Date Interval") ->
  JUDEW 
```

The original *JUD* tibble had `r nrow(JUD)` judicial charge records. Dropping
the records associated with offenders whose earliest testing window could not be
identified or that were coded *JCat12_Any* = 0 because *JCat12* = 999 (excluded 
user-missing) leaves `r nrow(JUDEW)` judicial charge records in *JUDEW*. Table
\ref{tab:examine_JUDEW_IWhen} shows how many judicial charge records were
associated with incidents that occurred before, during, and after the testing
window.

```{r examine_JUDEW_IWhen}
# Table caption.
TCap <- paste("Frequency Distribution of When the Incident Associated With A",
              "Judicial Charge Record Occurred Relative to Testing Window")
# Footnote text.
FN <- paste("Only judicial charge records for incidents with valid testing",
            "window start dates and offenses from the 12 crime categories", 
            "of interest were included. IWhen, when was incident relative", 
            "to testing window?")

# Vector of text values for column labels to be used in the table.
clabels <- c("IWhen", "Frequency", "Percent")

xtabs(~IWhen, data = JUDEW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(JUDEW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

Now, we need to get offender-level counts of judicial charge records associated
with incidents that occurred before, during, and after the testing window
respectively called *NJUD12_Before*, *NJUD12_During*, and *NJUD12_After*. We can
aggregate as follows to get them. We merge these variables into *IDNEW* too.
These new aggregated variables respect the criterion of counting only offenses
in the 12 main crime categories of interest because of the case selection that
went into building the *JUDEW* data.

```{r merge_Agg_NJUD_IWhen_IDNEW}
JUDEW %>% 
  mutate(NJUD12 = 1) %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  # Aggregate by OID and IWhen to get count variables
  summarize(NJUD12 = sum(NJUD12)) %>% 
  pivot_wider(names_from = IWhen, values_from = NJUD12, 
              names_glue = "NJUD12_{IWhen}") %>% 
  var_labels(NJUD12_Before = "No. of adjudicated charge records from 12 main crime categories before testing window",
             NJUD12_During = "No. of adjudicated charge records from 12 main crime categories during testing window",
             NJUD12_After  = "No. of adjudicated charge records from 12 main crime categories after testing window") %>% 
  # Merge adjudicated charge record count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(c("NJUD12_Before", "NJUD12_During", "NJUD12_After")), 
                .fns = replace_na, replace = 0)) %>% 
  # Compute alternate NJUD for records from 12 main crime categories.
  mutate(NJUD12 = NJUD12_Before + NJUD12_During + NJUD12_After) %>% 
  var_labels(NJUD12 = "No of judicial charge records from 12 main crime categories")->
  IDNEW
```

\FloatBarrier

## Merge Testing Window Variables Onto Conviction Records
The next step is to merge variables from *INCEW* onto the charge data in *CON*
so that we can classify each conviction record according to whether the
incident associated with it occurred before, during, or after the earliest
testing window for the offender by using *IWhen*. Then we subset down to the
*CON* records that have non-missing *WDate* values plus *JCat12_Any* = 1, then 
select only the variables we need to keep before saving a new tibble called
*CONEW*.

```{r create_CONEW}
INCEW %>% 
  # Retain only variables we need to merge into CON.
  select(IID, ESAKID, ESAK_IID, WDate, TWindow, IWhen) %>% 
  # Merge INCEW variables onto CON rows. 
  right_join(x = ., y = CON, by = "IID") %>% 
  # Retain only CON records for offenders with non-missing WDate values. 
  filter(is.na(WDate) == FALSE) %>% 
  # Retain only CON records for the main 12 crime categories, dropping 999.
  filter(JCat12_Any == 1) %>% 
  # Retain only variables we need, in sensible order. 
  select(all_of(c(names(JUD), twvars))) %>% 
  # Add a variable label that was otherwise being dropped. 
  var_labels(TWindow = "Testing Window Date Interval") ->
  CONEW 
```

The original *CON* tibble had `r nrow(CON)` conviction records. Dropping
the records associated with offenders whose earliest testing window could not be
identified or that were coded *JCat12_Any* = 0 because *JCat12* = 999 (excluded 
user-missing) leaves `r nrow(CONEW)` judicial charge records in *CONEW*. Table
\ref{tab:examine_CONEW_IWhen} shows how many conviction records were
associated with incidents that occurred before, during, and after the testing
window.

```{r examine_CONEW_IWhen}
# Table caption.
TCap <- paste("Frequency Distribution of When the Incident Associated With A",
              "Conviction Record Occurred Relative to Testing Window")
# Footnote text.
FN <- paste("Only conviction records for incidents with valid testing",
            "window start dates and offenses from the 12 crime categories", 
            "of interest were included. IWhen, when was incident relative", 
            "to testing window?")

# Vector of text values for column labels to be used in the table.
clabels <- c("IWhen", "Frequency", "Percent")

xtabs(~IWhen, data = CONEW) %>% 
  addmargins() %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(CONEW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

Now, we need to get offender-level counts of conviction records associated
with incidents that occurred before, during, and after the testing window
respectively called *NCON12_Before*, *NCON12_During*, and *NCON12_After*. We can
aggregate as follows to get them. We merge these variables into *IDNEW* too.
These new aggregated variables respect the criterion of counting only offenses
in the 12 main crime categories of interest because of the case selection that
went into building the *CONEW* data.

```{r merge_Agg_NCON_IWhen_IDNEW}
CONEW %>% 
  mutate(NCON12 = 1) %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  # Aggregate by OID and IWhen to get count variables
  summarize(NCON12 = sum(NCON12)) %>% 
  pivot_wider(names_from = IWhen, values_from = NCON12, 
              names_glue = "NCON12_{IWhen}") %>% 
  var_labels(NCON12_Before = "No. of conviction records from 12 main crime categories before testing window",
             NCON12_During = "No. of conviction records from 12 main crime categories during testing window",
             NCON12_After  = "No. of conviction records from 12 main crime categories after testing window") %>% 
  # Merge convicted charge record count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(c("NCON12_Before", "NCON12_During", "NCON12_After")), 
                .fns = replace_na, replace = 0)) %>% 
  # Compute alternate NCON for records from 12 main crime categories.
  mutate(NCON12 = NCON12_Before + NCON12_During + NCON12_After) %>% 
  var_labels(NCON12 = "No of conviction records from 12 main crime categories")->
  IDNEW
```
\FloatBarrier

## Aggregating Crime Category Dummy Variables to Incident Level Dummy Variables
We used the *dcode()* function to create the dummy coded crime category
variables while importing data from the SPSS data files into the *ARR*,
*CHG*, and *CON* tibbles, which were each subsequently modified and saved as the 
*ARREW*, *CHGEW*, and *CONEW* tibbles. 

In the *ARREW* tibble, the variables *ACat12_1* to *ACat12_12* and *ACat12_999*
mark which category of crime the offender was arrested for on a given arrest
offense record. The corresponding *CCat12_1* to *CCat12_12* and *CCat12_999*
variables in *CHGEW* show which crime category the individual was charged with
by a prosecuting attorney on a charge record. Meanwhile, *JCat12_1* to
*JCat12_12* and *JCat12_999* variables in *CONEW* show which crime category the
offender was convicted of on a given conviction record. 

Similarly, the *ACat12_Any*, *CCat12_Any*, and *JCat12_Any* dummy code variables
mark *ARREW*, *CHGEW*, and *CONEW* records that show an offender was
respectively arrested for, charged with, or convicted of one of the 12 main
crime categories of interest.

All three of those tibbles can have multiple records per criminal incident. This
section aggregates those dummy coded crime category variables from the record
level to the incident level to flag presence or absence of each crime category
on the incident. It merges the resulting variables onto the *INCEW* tibble.
That allows us to see which incidents were associated with arrests, charges,
and/or convictions for each category of crime or for any of the 12 main 
categories. 

The code chunk below creates objects containing vectors of variable names that 
can be used to simplify subsequent code. 

```{r create_acjvars}
# Create objects with vectors of variable names we need later. 
avars      <- paste("ACat12", c(1:12, 999, "Any"), sep = "_")
avarsb     <- paste0(avars, "_Before")
avarsd     <- paste0(avars, "_During")
avarsa     <- paste0(avars, "_After")
avarsbda   <- c(avarsb, avarsd, avarsa)
cvars      <- paste("CCat12", c(1:12, 999, "Any"), sep = "_")
cvarsb     <- paste0(cvars, "_Before")
cvarsd     <- paste0(cvars, "_During")
cvarsa     <- paste0(cvars, "_After")
cvarsbda   <- c(cvarsb, cvarsd, cvarsa)
jvars      <- paste("JCat12", c(1:12, 999, "Any"), sep = "_")
jvarsb     <- paste0(jvars, "_Before")
jvarsd     <- paste0(jvars, "_During")
jvarsa     <- paste0(jvars, "_After")
jvarsbda   <- c(jvarsb, jvarsd, jvarsa)
hxvars     <- paste("HXCat12", c(1:12, 999, "Any"), sep = "_")
hxvarsb    <- paste0(hxvars, "_Before")
hxvarsd    <- paste0(hxvars, "_During")
hxvarsa    <- paste0(hxvars, "_After")
hxvarsbda  <- c(hxvarsb, hxvarsd, hxvarsa)
```

As a reminder, the crime categories are shown in Table 
\ref{tab:crime_categories}, along with corresponding variable names. 

```{r crime_categories}
# Table caption.
TCap <- paste("Crime Category Labels and Names for Dummy Coded Variables From",
              "ARREW, CHGEW, and CONEW Data To be Merged Into INCEW Data")
# Footnote text.
FN <- paste("ARREW, variables pertaining to arrests;",
            "CHGEW, variables pertaining to prosecutor charges;",
            "CONEW, variables pertaining to convictions.")

# Create data for table.
CrimeCats <- data.frame(Label = c(get_labels(ARREW$ACat12), 
                                  "Any of 12 main categories (arson to weapons)"),
                        ARREW = avars,
                        CHGEW = cvars,
                        CONEW = jvars)

kable(CrimeCats, format = "latex", booktabs = TRUE, caption = TCap) %>% 
  add_header_above(c(" " = 1, "Source Datasets and Variable Names" = 3)) %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

### Incidents With Arrests
For any given incident (identifed by a unique value of *IID*), there can be
multiple arrest offense records in *ARREW*. The dummy variables *ACat12_1* to
*ACat12_12* and *ACat12_999* each mark whether or not a particular arrest
offense record was associated with a specific type of crime, while *ACat12_Any*
marks whether or not the arrest offense was associated any of the 12 main
categories of crime. Here, we aggregate them up to the incident level by taking
the maximum observed value for each incident. The resulting incident-level
records will have values of 1 for every crime category for which the offender
was arrested due to that incident and values of 0 for every crime category for
which the offender was not arrested due to that incident.

```{r merge_Agg_ACat12_INCEW}
# Aggregate ACat12 dummy codes by IID to incident level binary variables.
ARREW %>% 
  group_by(IID) %>% 
  summarize(across(.cols = all_of(avars), .fns = max)) %>% 
  # Merge dummy variables onto INCEW.
  left_join(x = INCEW, y = ., by = "IID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(avars), .fns = replace_na, replace = 0)) %>% 
  var_labels(ACat12_1   = "Arrested for arson",
             ACat12_2   = "Arrested for assault - DV, stalking",
             ACat12_3   = "Arrested for assault - non-sexual, non-DV",
             ACat12_4   = "Arrested for burglary",
             ACat12_5   = "Arrested for criminal sexual conduct",
             ACat12_6   = "Arrested for drug crime",
             ACat12_7   = "Arrested for homicide",
             ACat12_8   = "Arrested for larceny/theft/fraud",
             ACat12_9   = "Arrested for robbery", 
             ACat12_10  = "Arrested for sex crime, other excluding CSC",
             ACat12_11  = "Arrested for traffic/ordinances",
             ACat12_12  = "Arrested for weapons",
             ACat12_999 = "Arrested for excluded user-missing",
             ACat12_Any = "Arrested for any of 12 main crime categories") ->
  INCEW
```

### Incidents With Charges
For any given incident (identifed by a unique value of *IID*), there can be
multiple prosecutor charges records in *CHGEW*. The dummy variables *CCat12_1*
to *CCat12_12* and *CCat12_999* each mark whether or not a particular prosecutor
charge record was associated with a specific type of crime, while *CCat12_Any*
marks whether or not the charge was associated any of the 12 main categories of
crime. Here, we aggregate them up to the incident level by taking the maximum
observed value for each incident. The resulting incident-level records will have
values of 1 for every crime category for which the offender was charged due to
that incident and values of 0 for every crime category for which the offender
was not charged due to that incident.

```{r merge_Agg_CCat12_INCEW}         
# Aggregate CCat12 dummy codes by IID to incident level binary variables.
CHGEW %>% 
  group_by(IID) %>% 
  summarize(across(.cols = all_of(cvars), .fns = max))  %>% 
  # Merge dummy variables onto INCEW.
  left_join(x = INCEW, y = ., by = "IID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(cvars), .fns = replace_na, replace = 0)) %>% 
  var_labels(CCat12_1   = "Charged for arson",
             CCat12_2   = "Charged for assault - DV, stalking",
             CCat12_3   = "Charged for assault - non-sexual, non-DV",
             CCat12_4   = "Charged for burglary",
             CCat12_5   = "Charged for criminal sexual conduct",
             CCat12_6   = "Charged for drug crime",
             CCat12_7   = "Charged for homicide",
             CCat12_8   = "Charged for larceny/theft/fraud",
             CCat12_9   = "Charged for robbery", 
             CCat12_10  = "Charged for sex crime, other excluding CSC",
             CCat12_11  = "Charged for traffic/ordinances",
             CCat12_12  = "Charged for weapons",
             CCat12_999 = "Charged for excluded user-missing",
             CCat12_Any = "Charged for any of 12 main crime categories") ->
  INCEW
```

### Incidents With Convictions
For any given incident (identifed by a unique value of *IID*), there can be
multiple conviction records in *CONEW*. The dummy variables *JCat12_1* to
*JCat12_12* and *JCat12_999* each mark whether or not a particular adjudicated
conviction charge record was associated with a specific type of crime, while
*JCat12_Any* marks whether or not the charge was associated any of the 12 main
categories of crime. Here, we aggregate them up to the incident level by taking
the maximum observed value for each incident. The resulting incident-level
records will have values of 1 for every crime category for which the offender
was convicted due to that incident and values of 0 for every crime category for
which the offender was not convicted due to that incident.

```{r merge_Agg_JCat12_INCEW}
# Aggregate JCat12 dummy codes by IID to incident level binary variables.
CONEW %>% 
  group_by(IID) %>% 
  summarize(across(.cols = all_of(jvars), .fns = max)) %>% 
  # Merge dummy variables onto INCEW.
  left_join(x = INCEW, y = ., by = "IID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(jvars), .fns = replace_na, replace = 0)) %>% 
  var_labels(JCat12_1   = "Convicted for arson",
             JCat12_2   = "Convicted for assault - DV, stalking",
             JCat12_3   = "Convicted for assault - non-sexual, non-DV",
             JCat12_4   = "Convicted for burglary",
             JCat12_5   = "Convicted for criminal sexual conduct",
             JCat12_6   = "Convicted for drug crime",
             JCat12_7   = "Convicted for homicide",
             JCat12_8   = "Convicted for larceny/theft/fraud",
             JCat12_9   = "Convicted for robbery", 
             JCat12_10  = "Convicted for sex crime, other excluding CSC",
             JCat12_11  = "Convicted for traffic/ordinances",
             JCat12_12  = "Convicted for weapons",
             JCat12_999 = "Convicted for excluded user-missing",
             JCat12_Any = "Convicted for any of 12 main crime categories") ->
  INCEW
```

## Create Incident-Level Crime Category History Variables 
For each crime category, the *INCEW* dataset now contains three separate dummy
variables showing whether the offender was (a) arrested, (b) charged, or (c)
convicted of the offense associated with that category as a result of that
incident. However, we still need to create a single dummy variable for each
crime category that combines data across those three types of criminal history
events. The resulting set of history variables will be called *HXCat12_1* to
*HXCat12_12* and *HXCat12_999*. Values of 1 will mean the CHR data shows that
the offender was *arrested for, charged with, or convicted of* the offense in
question for that incident. It does not matter which of the three events
occurred: any one of them (and any combination of them) is sufficient to set
this value to 1. In contrast, a value of 0 will mean the CHR data shows that the
offender was *not arrested for, not charged with, and not convicted of* the
offense in question for that incident. The new variables will be added to the
*INCEW* dataset.

Meanwhile, the *HXCat12_Any* variable will show whether the offender was 
*arrested for, charged with, or convicted of* any of the 12 main categories of 
crime. 

```{r create_HXCat12_INCEW} 
INCEW %>% 
  # Create history variables
  mutate(HXCat12_1 = if_else(ACat12_1 + CCat12_1 + JCat12_1 >= 1, 
                              true = 1, false = 0),
         HXCat12_2 = if_else(ACat12_2 + CCat12_2 + JCat12_2 >= 1, 
                              true = 1, false = 0), 
         HXCat12_3 = if_else(ACat12_3 + CCat12_3 + JCat12_3 >= 1, 
                              true = 1, false = 0),
         HXCat12_4 = if_else(ACat12_4 + CCat12_4 + JCat12_4 >= 1, 
                              true = 1, false = 0),
         HXCat12_5 = if_else(ACat12_5 + CCat12_5 + JCat12_5 >= 1, 
                              true = 1, false = 0),
         HXCat12_6 = if_else(ACat12_6 + CCat12_6 + JCat12_6 >= 1, 
                              true = 1, false = 0),
         HXCat12_7 = if_else(ACat12_7 + CCat12_7 + JCat12_7 >= 1, 
                              true = 1, false = 0), 
         HXCat12_8 = if_else(ACat12_8 + CCat12_8 + JCat12_8 >= 1, 
                              true = 1, false = 0), 
         HXCat12_9 = if_else(ACat12_9 + CCat12_9 + JCat12_9 >= 1, 
                              true = 1, false = 0),
         HXCat12_10 = if_else(ACat12_10 + CCat12_10 + JCat12_10 >= 1, 
                              true = 1, false = 0),
         HXCat12_11 = if_else(ACat12_11 + CCat12_11 + JCat12_11 >= 1, 
                              true = 1, false = 0),
         HXCat12_12 = if_else(ACat12_12 + CCat12_12 + JCat12_12 >= 1, 
                              true = 1, false = 0),
         HXCat12_999 = if_else(ACat12_999 + CCat12_999 + JCat12_999 >= 1, 
                              true = 1, false = 0),
         HXCat12_Any = if_else(ACat12_Any + CCat12_Any + JCat12_Any >= 1, 
                              true = 1, false = 0)) %>% 
  var_labels(HXCat12_1 = "History shows arrested, charged, or convicted for arson",
             HXCat12_2 = "History shows arrested, charged, or convicted for assault - DV, stalking arrest",
             HXCat12_3 = "History shows arrested, charged, or convicted for assault - non-sexual, non-DV",
             HXCat12_4 = "History shows arrested, charged, or convicted for burglary",
             HXCat12_5 = "History shows arrested, charged, or convicted for criminal sexual conduct",
             HXCat12_6 = "History shows arrested, charged, or convicted for drug crime",
             HXCat12_7 = "History shows arrested, charged, or convicted for homicide",
             HXCat12_8 = "History shows arrested, charged, or convicted for larceny/theft/fraud ",
             HXCat12_9 = "History shows arrested, charged, or convicted for robbery",
             HXCat12_10 = "History shows arrested, charged, or convicted for sex crime - other, excludinng CSC",
             HXCat12_11 = "History shows arrested, charged, or convicted for traffic/ordinances",
             HXCat12_12 = "History shows arrested, charged, or convicted for weapons",
             HXCat12_999 = "History shows arrested, charged, or convicted for excluded user-missing",
             HXCat12_Any = "History shows arrested, charged, or convicted for any of 12 main crime categories") ->
  INCEW
```

Note that *HXCat12_5* is related to the existing variable *CSC_ANY* variable,
but a slightly more stringent definition because *HXCat12_5* codes incidents
that had adjudicated charges for CSC that were not convictions (and had no CSC
arrests and no CSC prosecutor charges) as 0, whereas *CSC_ANY* would code them
as 1. We will use *HXCat12_5* in the analyses for this paper instead of
*CSC_ANY*. Table \ref{tab:compare_HXCat12_5_to_CSC_ANY} shows how these two 
variables cross-tabulate. 

```{r compare_HXCat12_5_to_CSC_ANY}
# Table caption.
TCap <- paste0("Crosstabulate Incident-Level Criminal Sexual Conduct History ",
              "Variables (N = ", nrow(INCEW), ")")
# Footnote text.
FN <- paste("Only incident records for incidents with valid testing window",
            "start dates were included. The variables disagree when the only",
            "CHR data for CSC associated with the incident are adjudicated",
            "charge records that are not convictions.")

# Vector of text values for column labels to be used in the table.
clabels <- c("HXCat12_5", "CSC_ANY", "Frequency", "Percent")

xtabs(~HXCat12_5 + CSC_ANY, data = INCEW) %>% 
  as.data.frame() %>% 
  mutate(Percent = 100*Freq/nrow(INCEW)) %>% 
  kable(., format = "latex", booktabs = TRUE, caption = TCap, digits = 2,
        col.names = clabels, format.args = list(big.mark = ",")) %>% 
  column_spec(1:3, width = "1.5 cm") %>% 
  footnote(general = FN, general_title = "Note: ", footnote_as_chunk = TRUE,
         threeparttable = TRUE)
```

## Filter Incident Records 
Now we need to subset the *INCEW* data to contain only records for which
*HXCat12_Any* = 1 so that we only retain incidents associated where the offender
was offender was *arrested for, charged with, or convicted of* one or more of 
the 12 main crime categories.

```{r filter_INCEW}
INCEW %>% 
  filter(HXCat12_Any == 1) -> 
  INCEW
```

That reduces *INCEW* to `r nrow(INCEW)` records. 

## Aggregating Crime Category Dummy Variables to Offender Level Count Variables
Here we aggregate the dummy coded crime category variables data from the
incident level to offender level incident counts for each crime category. 

### Incidents With Arrests (Overall Plus Before, During, and After Testing Window)
For any given offender (identifed by an *OID* value), there can be multiple
incidents (identified by *IID* values). Aggregating the dummy variables ACat12_1
to ACat12_12 and ACat12_999 by summing across incidents for each offender allows
us to get overall incident counts showing how often the offender was arrested
for various types of crime over the course of the entire (documented) criminal
history. The aggregated variables merged into *IDNEW* retain the same variable
names as the source dummy-coded variables.
 
```{r merge_Agg_ACat12_IDNEW}
# Aggregate ACat12 dummy codes to offender level incident counts.
INCEW %>% 
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(avars), .fns = sum))  %>% 
  # Merge dummy variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(avars), .fns = replace_na, replace = 0)) %>% 
  var_labels(ACat12_1 = "No. incidents arrested for arson",
             ACat12_2 = "No. incidents arrested for assault - DV, stalking",
             ACat12_3 = "No. incidents arrested for assault - non-sexual, non-DV",
             ACat12_4 = "No. incidents arrested for burglary",
             ACat12_5 = "No. incidents arrested for criminal sexual conduct",
             ACat12_6 = "No. incidents arrested for drug crime",
             ACat12_7 = "No. incidents arrested for homicide",
             ACat12_8 = "No. incidents arrested for larceny/theft/fraud",
             ACat12_9 = "No. incidents arrested for robbery",
             ACat12_10 = "No. incidents arrested for sex crime - other, excluding CSC",
             ACat12_11 = "No. incidents arrested for traffic/ordinances",
             ACat12_12 = "No. incidents arrested for weapons",
             ACat12_999 = "No. incidents arrested for excluded user-missing", 
             ACat12_Any = "No. incidents arrested for any of 12 main crime categories") ->
  IDNEW
```

We also want to get separate counts for each crime category broken down by when
the incident occurred relative to the earliest testing window (*IWhen*). This
next chunk does that. The variable naming convention just adds suffixes to the
previously defined variable names to indicate the period to which each count
variable pertains.

```{r merge_Agg_ACat12_BDA_IDNEW}
# Aggregate ACat12 dummy codes to offender level incident counts by IWhen .
INCEW %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  pivot_wider(names_from = IWhen, values_from = all_of(avars), 
              values_fill = 0) %>%
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(avarsbda), .fns = sum, na.rm = TRUE))  %>% 
  # Merge count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  var_labels(ACat12_1_Before = "No. incidents arrested for arson before testing window before testing window",
             ACat12_2_Before = "No. incidents arrested for assault - DV, stalking before testing window",
             ACat12_3_Before = "No. incidents arrested for assault - non-sexual, non-DV before testing window",
             ACat12_4_Before = "No. incidents arrested for burglary before testing window",
             ACat12_5_Before = "No. incidents arrested for criminal sexual conduct before testing window",
             ACat12_6_Before = "No. incidents arrested for drug crime before testing window",
             ACat12_7_Before = "No. incidents arrested for homicide before testing window",
             ACat12_8_Before = "No. incidents arrested for larceny/theft/fraud before testing window",
             ACat12_9_Before = "No. incidents arrested for robbery before testing window",
             ACat12_10_Before = "No. incidents arrested for sex crime - other, excluding CSC before testing window",
             ACat12_11_Before = "No. incidents arrested for traffic/ordinances before testing window",
             ACat12_12_Before = "No. incidents arrested for weapons before testing window",
             ACat12_999_Before = "No. incidents arrested for excluded user-missing before testing window", 
             ACat12_Any_Before = "No. incidents arrested for any of 12 main crime categories before testing window",
             ACat12_1_During = "No. incidents arrested for arson during testing window",
             ACat12_2_During = "No. incidents arrested for assault - DV, stalking during testing window",
             ACat12_3_During = "No. incidents arrested for assault - non-sexual, non-DV during testing window",
             ACat12_4_During = "No. incidents arrested for burglary during testing window",
             ACat12_5_During = "No. incidents arrested for criminal sexual conduct during testing window",
             ACat12_6_During = "No. incidents arrested for drug crime during testing window",
             ACat12_7_During = "No. incidents arrested for homicide during testing window",
             ACat12_8_During = "No. incidents arrested for larceny/theft/fraud during testing window",
             ACat12_9_During = "No. incidents arrested for robbery during testing window",
             ACat12_10_During = "No. incidents arrested for sex crime - other, excluding CSC during testing window",
             ACat12_11_During = "No. incidents arrested for traffic/ordinances during testing window",
             ACat12_12_During = "No. incidents arrested for weapons during testing window",
             ACat12_999_During = "No. incidents arrested for excluded user-missing during testing window", 
             ACat12_Any_During = "No. incidents arrested for any of 12 main crime categories during testing window",
             ACat12_1_After = "No. incidents arrested for arson after testing window",
             ACat12_2_After = "No. incidents arrested for assault - DV, stalking after testing window",
             ACat12_3_After = "No. incidents arrested for assault - non-sexual, non-DV after testing window",
             ACat12_4_After = "No. incidents arrested for burglary after testing window",
             ACat12_5_After = "No. incidents arrested for criminal sexual conduct after testing window",
             ACat12_6_After = "No. incidents arrested for drug crime after testing window",
             ACat12_7_After = "No. incidents arrested for homicide after testing window",
             ACat12_8_After = "No. incidents arrested for larceny/theft/fraud after testing window",
             ACat12_9_After = "No. incidents arrested for robbery after testing window",
             ACat12_10_After = "No. incidents arrested for sex crime - other, excluding CSC after testing window",
             ACat12_11_After = "No. incidents arrested for traffic/ordinances after testing window",
             ACat12_12_After = "No. incidents arrested for weapons after testing window",
             ACat12_999_After = "No. incidents arrested for excluded user-missing", 
             ACat12_Any_After = "No. incidents arrested for any of 12 main crime categories after testing window") -> 
  IDNEW
```

### Incidents With Charges (Overall Plus Before, During, and After Testing Window)
For any given offender (identifed by an *OID* value), there can be multiple
incidents (identified by *IID* values). Aggregating the dummy variables CCat12_1
to CCat12_12 and CCat12_999 by summing across incidents for each offender allows
us to get overall incident counts showing how often the offender was charged
for various types of crime over the course of the entire (documented) criminal
history. The aggregated variables merged into *IDNEW* retain the same varable
names as the source dummy-coded variables.
 
```{r merge_Agg_CCat12_IDNEW}
# Aggregate CCat12 dummy codes to offender level incident counts.
INCEW %>% 
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(cvars), .fns = sum))  %>% 
  # Merge dummy variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(cvars), .fns = replace_na, replace = 0)) %>% 
  var_labels(CCat12_1 = "No. incidents charged for arson",
             CCat12_2 = "No. incidents charged for assault - DV, stalking",
             CCat12_3 = "No. incidents charged for assault - non-sexual, non-DV",
             CCat12_4 = "No. incidents charged for burglary",
             CCat12_5 = "No. incidents charged for criminal sexual conduct",
             CCat12_6 = "No. incidents charged for drug crime",
             CCat12_7 = "No. incidents charged for homicide",
             CCat12_8 = "No. incidents charged for larceny/theft/fraud",
             CCat12_9 = "No. incidents charged for robbery",
             CCat12_10 = "No. incidents charged for sex crime - other, excluding CSC",
             CCat12_11 = "No. incidents charged for traffic/ordinances",
             CCat12_12 = "No. incidents charged for weapons",
             CCat12_999 = "No. incidents charged for excluded user-missing", 
             CCat12_Any = "No. incidents charged for any of 12 main crime categories") ->
  IDNEW
```

We also want to get separate counts for each crime category broken down by when
the incident occurred relative to the earliest testing window (*IWhen*). This
next chunk does that. The variable naming convention just adds suffixes to the
previously defined variable names to indicate the period to which each count
variable pertains.

```{r merge_Agg_CCat12_BDA_IDNEW}
# Aggregate CCat12 dummy codes to offender level incident counts by IWhen .
INCEW %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  pivot_wider(names_from = IWhen, values_from = all_of(cvars), 
              values_fill = 0) %>%
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(cvarsbda), .fns = sum, na.rm = TRUE))  %>% 
  # Merge count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  var_labels(CCat12_1_Before = "No. incidents charged for arson before testing window before testing window",
             CCat12_2_Before = "No. incidents charged for assault - DV, stalking before testing window",
             CCat12_3_Before = "No. incidents charged for assault - non-sexual, non-DV before testing window",
             CCat12_4_Before = "No. incidents charged for burglary before testing window",
             CCat12_5_Before = "No. incidents charged for criminal sexual conduct before testing window",
             CCat12_6_Before = "No. incidents charged for drug crime before testing window",
             CCat12_7_Before = "No. incidents charged for homicide before testing window",
             CCat12_8_Before = "No. incidents charged for larceny/theft/fraud before testing window",
             CCat12_9_Before = "No. incidents charged for robbery before testing window",
             CCat12_10_Before = "No. incidents charged for sex crime - other, excluding CSC before testing window",
             CCat12_11_Before = "No. incidents charged for traffic/ordinances before testing window",
             CCat12_12_Before = "No. incidents charged for weapons before testing window",
             CCat12_999_Before = "No. incidents charged for excluded user-missing before testing window", 
             CCat12_Any_Before = "No. incidents charged for any of 12 main crime categories before testing window",
             CCat12_1_During = "No. incidents charged for arson during testing window",
             CCat12_2_During = "No. incidents charged for assault - DV, stalking during testing window",
             CCat12_3_During = "No. incidents charged for assault - non-sexual, non-DV during testing window",
             CCat12_4_During = "No. incidents charged for burglary during testing window",
             CCat12_5_During = "No. incidents charged for criminal sexual conduct during testing window",
             CCat12_6_During = "No. incidents charged for drug crime during testing window",
             CCat12_7_During = "No. incidents charged for homicide during testing window",
             CCat12_8_During = "No. incidents charged for larceny/theft/fraud during testing window",
             CCat12_9_During = "No. incidents charged for robbery during testing window",
             CCat12_10_During = "No. incidents charged for sex crime - other, excluding CSC during testing window",
             CCat12_11_During = "No. incidents charged for traffic/ordinances during testing window",
             CCat12_12_During = "No. incidents charged for weapons during testing window",
             CCat12_999_During = "No. incidents charged for excluded user-missing during testing window", 
             CCat12_Any_During = "No. incidents charged for any of 12 main crime categories during testing window",
             CCat12_1_After = "No. incidents charged for arson after testing window",
             CCat12_2_After = "No. incidents charged for assault - DV, stalking after testing window",
             CCat12_3_After = "No. incidents charged for assault - non-sexual, non-DV after testing window",
             CCat12_4_After = "No. incidents charged for burglary after testing window",
             CCat12_5_After = "No. incidents charged for criminal sexual conduct after testing window",
             CCat12_6_After = "No. incidents charged for drug crime after testing window",
             CCat12_7_After = "No. incidents charged for homicide after testing window",
             CCat12_8_After = "No. incidents charged for larceny/theft/fraud after testing window",
             CCat12_9_After = "No. incidents charged for robbery after testing window",
             CCat12_10_After = "No. incidents charged for sex crime - other, excluding CSC after testing window",
             CCat12_11_After = "No. incidents charged for traffic/ordinances after testing window",
             CCat12_12_After = "No. incidents charged for weapons after testing window",
             CCat12_999_After = "No. incidents charged for excluded user-missing", 
             CCat12_Any_After = "No. incidents charged for any of 12 main crime categories after testing window") -> 
  IDNEW
```

### Incidents With Convictions (Overall Plus Before, During, and After Testing Window)
For any given offender (identifed by an *OID* value), there can be multiple
incidents (identified by *IID* values). Aggregating the dummy variables CCat12_1
to CCat12_12 and CCat12_999 by summing across incidents for each offender allows
us to get overall incident counts showing how often the offender was convicted
for various types of crime over the course of the entire (documented) criminal
history. The aggregated variables merged into *IDNEW* retain the same varable
names as the source dummy-coded variables.
 
```{r merge_Agg_JCat12_IDNEW}
# Aggregate JCat12 dummy codes to offender level incident counts.
INCEW %>% 
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(jvars), .fns = sum))  %>% 
  # Merge dummy variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(jvars), .fns = replace_na, replace = 0)) %>% 
  var_labels(JCat12_1 = "No. incidents convicted for arson",
             JCat12_2 = "No. incidents convicted for assault - DV, stalking",
             JCat12_3 = "No. incidents convicted for assault - non-sexual, non-DV",
             JCat12_4 = "No. incidents convicted for burglary",
             JCat12_5 = "No. incidents convicted for criminal sexual conduct",
             JCat12_6 = "No. incidents convicted for drug crime",
             JCat12_7 = "No. incidents convicted for homicide",
             JCat12_8 = "No. incidents convicted for larceny/theft/fraud",
             JCat12_9 = "No. incidents convicted for robbery",
             JCat12_10 = "No. incidents convicted for sex crime - other, excluding CSC",
             JCat12_11 = "No. incidents convicted for traffic/ordinances",
             JCat12_12 = "No. incidents convicted for weapons",
             JCat12_999 = "No. incidents convicted for excluded user-missing", 
             JCat12_Any = "No. incidents convicted for any of 12 main crime categories") ->
  IDNEW
```

We also want to get separate counts for each crime category broken down by when
the incident occurred relative to the earliest testing window (*IWhen*). This
next chunk does that. The variable naming convention just adds suffixes to the
previously defined variable names to indicate the period to which each count
variable pertains.

```{r merge_Agg_JCat12_BDA_IDNEW}
# Aggregate JCat12 dummy codes to offender level incident counts by IWhen.
INCEW %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  pivot_wider(names_from = IWhen, values_from = all_of(jvars), 
              values_fill = 0) %>%
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(jvarsbda), .fns = sum, na.rm = TRUE))  %>% 
  # Merge count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  var_labels(JCat12_1_Before = "No. incidents convicted for arson before testing window before testing window",
             JCat12_2_Before = "No. incidents convicted for assault - DV, stalking before testing window",
             JCat12_3_Before = "No. incidents convicted for assault - non-sexual, non-DV before testing window",
             JCat12_4_Before = "No. incidents convicted for burglary before testing window",
             JCat12_5_Before = "No. incidents convicted for criminal sexual conduct before testing window",
             JCat12_6_Before = "No. incidents convicted for drug crime before testing window",
             JCat12_7_Before = "No. incidents convicted for homicide before testing window",
             JCat12_8_Before = "No. incidents convicted for larceny/theft/fraud before testing window",
             JCat12_9_Before = "No. incidents convicted for robbery before testing window",
             JCat12_10_Before = "No. incidents convicted for sex crime - other, excluding CSC before testing window",
             JCat12_11_Before = "No. incidents convicted for traffic/ordinances before testing window",
             JCat12_12_Before = "No. incidents convicted for weapons before testing window",
             JCat12_999_Before = "No. incidents convicted for excluded user-missing before testing window", 
             JCat12_Any_Before = "No. incidents convicted for any of 12 main crime categories before testing window",
             JCat12_1_During = "No. incidents convicted for arson during testing window",
             JCat12_2_During = "No. incidents convicted for assault - DV, stalking during testing window",
             JCat12_3_During = "No. incidents convicted for assault - non-sexual, non-DV during testing window",
             JCat12_4_During = "No. incidents convicted for burglary during testing window",
             JCat12_5_During = "No. incidents convicted for criminal sexual conduct during testing window",
             JCat12_6_During = "No. incidents convicted for drug crime during testing window",
             JCat12_7_During = "No. incidents convicted for homicide during testing window",
             JCat12_8_During = "No. incidents convicted for larceny/theft/fraud during testing window",
             JCat12_9_During = "No. incidents convicted for robbery during testing window",
             JCat12_10_During = "No. incidents convicted for sex crime - other, excluding CSC during testing window",
             JCat12_11_During = "No. incidents convicted for traffic/ordinances during testing window",
             JCat12_12_During = "No. incidents convicted for weapons during testing window",
             JCat12_999_During = "No. incidents convicted for excluded user-missing during testing window", 
             JCat12_Any_During = "No. incidents convicted for any of 12 main crime categories during testing window",
             JCat12_1_After = "No. incidents convicted for arson after testing window",
             JCat12_2_After = "No. incidents convicted for assault - DV, stalking after testing window",
             JCat12_3_After = "No. incidents convicted for assault - non-sexual, non-DV after testing window",
             JCat12_4_After = "No. incidents convicted for burglary after testing window",
             JCat12_5_After = "No. incidents convicted for criminal sexual conduct after testing window",
             JCat12_6_After = "No. incidents convicted for drug crime after testing window",
             JCat12_7_After = "No. incidents convicted for homicide after testing window",
             JCat12_8_After = "No. incidents convicted for larceny/theft/fraud after testing window",
             JCat12_9_After = "No. incidents convicted for robbery after testing window",
             JCat12_10_After = "No. incidents convicted for sex crime - other, excluding CSC after testing window",
             JCat12_11_After = "No. incidents convicted for traffic/ordinances after testing window",
             JCat12_12_After = "No. incidents convicted for weapons after testing window",
             JCat12_999_After = "No. incidents convicted for excluded user-missing", 
             JCat12_Any_After = "No. incidents convicted for any of 12 main crime categories after testing window") -> 
  IDNEW
```

### Incidents with Any History (Arrest, Charge, or Conviction)
Having created the crime category history variables at the incident level, next
we aggregate them to offender-level incident count varaiables named *HXCat12_1* 
to *HXCat12_12* and *HXCat12_999*. Each of these will contain the number of 
incidents that had a history showing the offender was 
*arrested for, charged with, or convicted of* the offense in question. 

Aggregating the *INCEW* data on HXCat12_Any to offender-level record counts and 
merging them onto *IDNEW* effectively creates creates an alternate version of 
*NINC* called *HXCat12_Any* that only counts records associated with incidents 
where the offender was *arrested for, charged with, or convicted of* one or more
of the 12 main crime categories. 

```{r merge_Agg_HXCat12_IDNEW} 
INCEW %>% 
  group_by(OID, .drop = FALSE) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(hxvars), .fns = sum))  %>% 
  # Merge count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  # Replace all NA values in the new variables with 0. 
  mutate(across(.cols = all_of(hxvars), .fns = replace_na, replace = 0)) %>% 
  var_labels(HXCat12_1 = "No. incidents arrested, charged, or convicted for arson",
             HXCat12_2 = "No. incidents arrested, charged, or convicted for assault - DV, stalking",
             HXCat12_3 = "No. incidents arrested, charged, or convicted for assault - non-sexual, non-DV",
             HXCat12_4 = "No. incidents arrested, charged, or convicted for burglary",
             HXCat12_5 = "No. incidents arrested, charged, or convicted for criminal sexual conduct",
             HXCat12_6 = "No. incidents arrested, charged, or convicted for drug crime",
             HXCat12_7 = "No. incidents arrested, charged, or convicted for homicide",
             HXCat12_8 = "No. incidents arrested, charged, or convicted for larceny/theft/fraud",
             HXCat12_9 = "No. incidents arrested, charged, or convicted for robbery",
             HXCat12_10 = "No. incidents arrested, charged, or convicted for sex crime - other, excluding CSC",
             HXCat12_11 = "No. incidents arrested, charged, or convicted for traffic/ordinances",
             HXCat12_12 = "No. incidents arrested, charged, or convicted for weapons",
             HXCat12_999 = "No. incidents arrested, charged, or convicted for excluded user-missing", 
             HXCat12_Any = "No. incidents arrested, charged, or convicted for any of 12 main crime categories") ->
  IDNEW
```

Now, we need to get offender-level breakdowns of those incident counts for 
incidents that occurred before, during, and after the testing window. We can 
aggregate as follows to get them and merge them into *IDNEW*. 

This means that *HXCat12_Any_Before*, *HXCat12_Any_During*, and
*HXCat12_Any_After* are respectively alternate versions of *NINC_Before*,
*NINC_During*, and *NINC_After* that only count records associated with
incidents where the offender was *arrested for, charged with, or convicted of*
one or more of the 12 main crime categories.

```{r merge_Agg_HXCat12_BDA_IDNEW} 
# Aggregate HXCat12 dummy codes to offender level incident counts by IWhen.
INCEW %>% 
  group_by(OID, IWhen, .drop = FALSE) %>% 
  pivot_wider(names_from = IWhen, values_from = all_of(hxvars), 
              values_fill = 0) %>%
  group_by(OID) %>% 
  # Aggregate dummy codes by OID into incident count variables
  summarize(across(.cols = all_of(hxvarsbda), .fns = sum, na.rm = TRUE))  %>% 
  # Merge count variables onto IDNEW.
  left_join(x = IDNEW, y = ., by = "OID") %>% 
  var_labels(HXCat12_1_Before = "No. incidents arrested, charged, or convicted for arson before testing window",
             HXCat12_2_Before = "No. incidents arrested, charged, or convicted for assault - DV, stalking before testing window",
             HXCat12_3_Before = "No. incidents arrested, charged, or convicted for assault - non-sexual, non-DV before testing window ",
             HXCat12_4_Before = "No. incidents arrested, charged, or convicted for burglary before testing window",
             HXCat12_5_Before = "No. incidents arrested, charged, or convicted for criminal sexual conduct before testing window",
             HXCat12_6_Before = "No. incidents arrested, charged, or convicted for drug crime before testing window",
             HXCat12_7_Before = "No. incidents arrested, charged, or convicted for homicide before testing window",
             HXCat12_8_Before = "No. incidents arrested, charged, or convicted for larceny/theft/fraud before testing window",
             HXCat12_9_Before = "No. incidents arrested, charged, or convicted for robbery before testing window",
             HXCat12_10_Before = "No. incidents arrested, charged, or convicted for sex crime - other, excluding CSC before testing window",
             HXCat12_11_Before = "No. incidents arrested, charged, or convicted for traffic/ordinances before testing window",
             HXCat12_12_Before = "No. incidents arrested, charged, or convicted for weapons before testing window",
             HXCat12_999_Before = "No. incidents arrested, charged, or convicted for excluded user-missing before testing window",
             HXCat12_Any_Before = "No. incidents arrested, charged, or convicted for any of 12 main crime categories before testing window",
             HXCat12_1_During = "No. incidents arrested, charged, or convicted for arson during testing window",
             HXCat12_2_During = "No. incidents arrested, charged, or convicted for assault - DV, stalking during testing window",
             HXCat12_3_During = "No. incidents arrested, charged, or convicted for assault - non-sexual, non-DV during testing window",
             HXCat12_4_During = "No. incidents arrested, charged, or convicted for burglary during testing window",
             HXCat12_5_During = "No. incidents arrested, charged, or convicted for criminal sexual conduct during testing window",
             HXCat12_6_During = "No. incidents arrested, charged, or convicted for drug crime during testing window",
             HXCat12_7_During = "No. incidents arrested, charged, or convicted for homicide during testing window",
             HXCat12_8_During = "No. incidents arrested, charged, or convicted for larceny/theft/fraud during testing window",
             HXCat12_9_During = "No. incidents arrested, charged, or convicted for robbery during testing window",
             HXCat12_10_During = "No. incidents arrested, charged, or convicted for sex crime - other, excluding CSC during testing window",
             HXCat12_11_During = "No. incidents arrested, charged, or convicted for traffic/ordinances during testing window",
             HXCat12_12_During = "No. incidents arrested, charged, or convicted for weapons during testing window",
             HXCat12_999_During = "No. incidents arrested, charged, or convicted for excluded user-missing during testing window",
             HXCat12_Any_During = "No. incidents arrested, charged, or convicted for any of 12 main crime categories during testing window",
             HXCat12_1_After = "No. incidents arrested, charged, or convicted for arson after testing window",
             HXCat12_2_After = "No. incidents arrested, charged, or convicted for assault - DV, stalking after testing window",
             HXCat12_3_After = "No. incidents arrested, charged, or convicted for assault - non-sexual, non-DV after testing window",
             HXCat12_4_After = "No. incidents arrested, charged, or convicted for burglary after testing window",
             HXCat12_5_After = "No. incidents arrested, charged, or convicted for criminal sexual conduct after testing window",
             HXCat12_6_After = "No. incidents arrested, charged, or convicted for drug crime after testing window",
             HXCat12_7_After = "No. incidents arrested, charged, or convicted for homicide after testing window",
             HXCat12_8_After = "No. incidents arrested, charged, or convicted for larceny/theft/fraud after testing window",
             HXCat12_9_After = "No. incidents arrested, charged, or convicted for robbery after testing window",
             HXCat12_10_After = "No. incidents arrested, charged, or convicted for sex crime - other, excluding CSC after testing window",
             HXCat12_11_After = "No. incidents arrested, charged, or convicted for traffic/ordinances after testing window",
             HXCat12_12_After = "No. incidents arrested, charged, or convicted for weapons after testing window",
             HXCat12_999_After = "No. incidents arrested, charged, or convicted for excluded user-missing after testing window",
             HXCat12_Any_After = "No. incidents arrested, charged, or convicted for any of 12 main crime categories after testing window") ->
  IDNEW
```

# Compute Crime Category Count Variables in IDNEW
Here we compute the number of crime categories for which an offender was (a) 
arrested, (b) charged, (c) convicted, and (d) arrested, charged, or convicted. 
We store separate variables for overall counts, and counts broken down by when 
the incidents occurred relative to the testing window (*IWhen*). 

```{r update_IDNEW}
IDNEW %>% 
  # Count the number of crime categories associated w/ each offender.
  rowwise() %>% 
  mutate(ACat12_Count = sum(c_across(all_of(avars[1:12])) > 0),
         ACat12_Count_Before = sum(c_across(all_of(avarsb[1:12])) > 0),
         ACat12_Count_During = sum(c_across(all_of(avarsd[1:12])) > 0),
         ACat12_Count_After = sum(c_across(all_of(avarsa[1:12])) > 0),
         CCat12_Count = sum(c_across(all_of(cvars[1:12])) > 0),
         CCat12_Count_Before = sum(c_across(all_of(cvarsb[1:12])) > 0),
         CCat12_Count_During = sum(c_across(all_of(cvarsd[1:12])) > 0),
         CCat12_Count_After = sum(c_across(all_of(cvarsa[1:12])) > 0),
         JCat12_Count = sum(c_across(all_of(jvars[1:12])) > 0),
         JCat12_Count_Before = sum(c_across(all_of(jvarsb[1:12])) > 0),
         JCat12_Count_During = sum(c_across(all_of(jvarsd[1:12])) > 0),
         JCat12_Count_After = sum(c_across(all_of(jvarsa[1:12])) > 0),
         HXCat12_Count = sum(c_across(all_of(hxvars[1:12])) > 0),
         HXCat12_Count_Before = sum(c_across(all_of(hxvarsb[1:12])) > 0),
         HXCat12_Count_During = sum(c_across(all_of(hxvarsd[1:12])) > 0),
         HXCat12_Count_After = sum(c_across(all_of(hxvarsa[1:12])) > 0)) %>% 
  var_labels(ACat12_Count = "Arrested crime category count (overall)",
             ACat12_Count_Before = "Arrested crime category count (incidents before testing window)",
             ACat12_Count_During = "Arrested crime category count (incidents during testing window)",
             ACat12_Count_After = "Arrested crime category count (incidents after testing window)",
             CCat12_Count = "Charged crime category count (overall)",
             CCat12_Count_Before = "Charged crime category count (incidents before testing window)",
             CCat12_Count_During = "Charged crime category count (incidents during testing window)",
             CCat12_Count_After = "Charged crime category count (incidents after testing window)",
             JCat12_Count = "Convicted crime category count (overall)",
             JCat12_Count_Before = "Convicted crime category count (incidents before testing window)",
             JCat12_Count_During = "Convicted crime category count (incidents during testing window)",
             JCat12_Count_After = "Convicted crime category count (incidents after testing window)",
             HXCat12_Count = "Arrested, charged, or convicted crime category count (overall)",
             HXCat12_Count_Before = "Arrested, charged, or convicted crime category count (incidents before testing window)",
             HXCat12_Count_During = "Arrested, charged, or convicted crime category count (incidents during testing window)",
             HXCat12_Count_After = "Arrested, charged, or convicted crime category count (incidents after testing window)") -> 
  IDNEW
```

# Check Assumptions
We actually have few redundant incident count variables in *IDNEW* now. The
variables OCSC1, OCSC2, and OCSC3 were created and stored in the SPSS file
during the original grant work. The variables ACat12_5, CCat12_5, and JCat12_5
respectively contain exactly the same data, but were created above in the 
**Aggregating Crime Category Variables** section. They should agree with one
another and we can check that as follows to prove that the aggregation logic was
implemented the same way.

```{r check_assumptions}
# Verify that OCSC1 = ACat12_5, OCSC2 = CCat12_5, & OCSC3 = JCat12_5.
all(IDNEW$OCSC1 == IDNEW$ACat12_5) # Arrest incident counts
all(IDNEW$OCSC2 == IDNEW$CCat12_5) # Charge incident counts
all(IDNEW$OCSC3 == IDNEW$JCat12_5) # Conviction incident counts
```

# Criminal History Record (CHR) Count Overview
Below is a summary of the record counts for different types of CHR records, 
along with the numbers of unique incidents and unique offenders represented in
those records. It also shows the range of event dates associated with each 
record type (i.e., birth, incident, arrest, charge, and adjudication dates). 

```{r chr_overview, warning = FALSE}
# Table caption.
TCap <- paste("Criminal History Record Counts and Date Ranges Before Versus",
              "After Case Selection")

# Summarize record counts before & after case selection for this study.
bind_rows(dfsummary(IDN, label = "Offenders...Before", dvar = IDN$DOB),
          dfsummary(IDNEW, label = "Offenders...After", dvar = IDNEW$DOB),
          dfsummary(INC, label = "Incidents...Before", dvar = INC$IDate), 
          dfsummary(INCEW, label = "Incidents...After", dvar = INCEW$IDate), 
          dfsummary(ARR, label = "Arrest offenses...Before", dvar = ARR$ADate),
          dfsummary(ARREW, label = "Arrest offenses...After", 
                    dvar = ARREW$ADate),
          dfsummary(CHG, label = "Prosecutor charges...Before", 
                    dvar = CHG$CDate),
          dfsummary(CHGEW, label = "Prosecutor charges...After", 
                    dvar = CHGEW$CDate),
          dfsummary(JUD, label = "Adjudicated charges (all dispositions)...Before", 
                    dvar = JUD$JDate),
          dfsummary(JUDEW, label = "Adjudicated charges (all dispositions)...After", 
                    dvar = JUDEW$JDate),
          dfsummary(CON, label = "Adjudicated charges (convictions)...Before", 
                    dvar = CON$JDate),
          dfsummary(CONEW, label = "Adjudicated charges (convictions)...After", 
                    dvar = CONEW$JDate)) ->
  CHR.RC
kable(CHR.RC, format = "latex", booktabs = TRUE, caption = TCap, 
      format.args = list(big.mark = ','))
```

\FloatBarrier

# Save Data to a File

```{r save_data}
save(IDNEW, INCEW, ARREW, CHGEW, JUDEW, CONEW, 
     file = here::here("./data/CHR_Data.RData"))
```

# Wrap Up

\FloatBarrier

## Project Information
These materials are scholarly products based on research funded by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (01/01/2015–12/31/2018). Serial sexual
assaults: A longitudinal examination of offending patterns using DNA evidence.
[NIJ Award # 2014-NE-BX-0006, Awarded, $699,533]. Sponsor: National Institute of
Justice. Location: Michigan State University, East Lansing, MI.

\FloatBarrier

## References
Campbell, R. (2019). *Serial sexual assaults: A longitudinal examination of
offending patterns using DNA evidence, Detroit, Michigan, 2009* [Data files,
codebooks, computer programs, and statistical output]. ICPSR37134-v1. Ann Arbor,
MI: Inter-university Consortium for Political and Social Research [distributor],
2019-02-28. Retrieved from: https://doi.org/10.3886/ICPSR37134.v1

\FloatBarrier

## Software Information
We use R Markdown to enhance reproducibility. Knitting the source R Markdown 
script *`r knitr:::current_input()`* generates this PDF file containing 
explanatory text, R code, plus R output (text and graphics).

- We used [RStudio](www.rstudio.org) `r rstudioapi::versionInfo()$version` to 
  work with R and R markdown files. The software chain looks like this:
  **Rmd file > RStudio > R > rmarkdown > knitr > pandoc > TinyTeX or MiKTeX > PDF file**.
- We recommend using [TinyTeX](https://yihui.org/tinytex/) to compile LaTeX files 
  into PDF files. However, it should be viable to use 
  [MiKTeX version 2.9](https://miktex.org) instead. 
- We used [pandoc](https://pandoc.org) `r pandoc_version()` for this 
  document. 

This document was generated using the following computational environment and 
dependencies: 

``` {r show_citations}
# If is_tineytex = TRUE, then we used TinyTeX, otherwise we used MikTeX. 
tinytex:::is_tinytex()

# Get R and R package version numbers in use.
devtools::session_info()
```

The current Git commit details and status are:

```{r git_details, eval=TRUE}
# Store whether git2r is installed and we are in a git repository.
GitCheck <- "git2r" %in% installed.packages() & git2r::in_repository(path = ".")
if(!GitCheck) cat(paste0("GitCheck = ", GitCheck, 
                         ". Version control details not available. \n"))

# What commit is this file at? 
if (GitCheck) git2r::repository(here::here())

# What is the repository status? 
if (GitCheck) git2r::status()
```
