---
title: \sffamily{\bfseries{\LARGE Criminal History Records Paper Step 1 (Data Management)}}
geometry: "left=.5in,right=.5in,top=.75in,bottom=.75in"
author: "Steven J. Pierce"
output:
 pdf_document:
   latex_engine: xelatex
   number_sections: true
   toc: yes
   toc_depth: 3
   includes:
     in_header: "../compact-title.tex"
urlcolor: blue
header-includes:
- \usepackage{fancyhdr}
- \usepackage[yyyymmdd,hhmmss]{datetime}
- \usepackage{lastpage}
- \usepackage{fontspec}
- \defaultfontfeatures{Ligatures=TeX}
- \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
- \usepackage{url}
- \usepackage{floatrow}
- \floatplacement{figure}{!ht}
- \floatplacement{table}{!ht}
- \usepackage{placeins}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{dcolumn}
- \usepackage{titling}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}}
- \pagestyle{fancy}
- \lhead{SSA CHR Paper Step 1 Data Mgt}
- \rhead{\today\ \currenttime}
- \lfoot{\texttt{\small \detokenize{`r sub(".Rmd", ".pdf", knitr:::current_input(dir = FALSE))`}}} 
- \cfoot{ }
- \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0.4pt}
- \renewcommand{\footrulewidth}{0.4pt}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

********************************************************************************  
\FloatBarrier

# Purpose.
This file imports copies of publicly archived data files (Campbell, 2019) into 
R, then performs data management to prepare a new data file for a descriptive 
paper about the criminal histories of suspected serial sexual offenders.  


\FloatBarrier

# Setup
Set global R chunk options (local chunk options will over-ride global options). 

``` {r global_options}
# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)
```

If you have not already done so, install the piercer package from 
[GitHub](https://github.com/sjpierce/piercer) by running the next chunk of R 
code. The chunk is set to eval = FALSE so that you have to manually run that 
code, which you should only need to do once (or whenever the piercer package 
has been updated). 

```{r, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("sjpierce/piercer")
```

Load R packages that we need to get additional functions. 

``` {r load_packages}
library(here)         # for here()
library(dplyr)        # for %>%, filter(), group_by(), & summarise()
library(tidyr)        # for arrange(), filter(), group_by(), mutate(), spread(), 
                      # summarise(), %>%, etc. 
library(rmarkdown)    # for render()
library(knitr)        # for kable()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)   # for kable_styling(), add_header_above(), column_spec(),
                      # collapse_rows(), and landscape()
library(descr)            # For freq().
options(descr.plot=FALSE) # Make freq() & crosstab() skip plots by default.
library(lubridate)        # For date conversion, eg. ymd(), time_length().
library(sjlabelled) # For set_label(), get_label()
library(haven)      # for read_spss()
library(lattice)          # For xyplot(), bwplot(), etc. 
library(piercer)    # for DI() and tag_um()
library(plyr)             # For mapvalues()
library(psych)            # For describe()
library(car)              # For recode()
```

Create objects to hold objects with settings we want to reuse. 

```{r my_settings}
# Custom settings for use with bwplot().
my.boxes <- list(box.rectangle = list(col = "black", lwd = 2), 
                 box.umbrella = list(col = "black", lwd = 2))
```

\FloatBarrier

# Import Files
The SPSS files we will need to import, plus docmentation about their contents
and relationships between them, are available from an online archive (Campbell,
2019).

\FloatBarrier

## Core Criminal History Records (CHR) Files
Import the SPSS data files for the five core types of records comprising
Michigan criminal history records (CHR): offenders (IDN), incidents (INC),
arrest offenses (ARR), prosecutor charges (CHG), and judicial charges (JUD). 
See Campbell (2019) for details on these files. 

``` {r import_chr}
# Read SPSS data files.
IDN <- read_sav("data/SSA_IDN_Offenders_2018-09-03.sav", user_na = TRUE)
INC <- read_sav("data/SSA_INC_Incidents_Imputed_2018-09-03.sav", user_na = TRUE)
ARR <- read_sav("data/SSA_ARR_Arrests_Imputed_2018-09-03.sav", user_na = TRUE)
CHG <- read_sav("data/SSA_CHG_PA_Charges_Imputed_2018-09-03.sav", 
                user_na = TRUE)
JUD <- read_sav("data/SSA_JUD_Judicial_Charges_Imputed_2018-09-03.sav", 
                user_na = TRUE) 

# Replace user-missing value labels that have parentheses in them so they will
# work correctly in freq() as user.missing arguments. 
ARR$ACat12 <- rvlabel(ARR$ACat12)
ARR$ACat10 <- rvlabel(ARR$ACat10)
ARR$ACat04 <- rvlabel(ARR$ACat04)
ARR$ACat03 <- rvlabel(ARR$ACat03)
CHG$CCat12 <- rvlabel(CHG$CCat12)
CHG$CCat10 <- rvlabel(CHG$CCat10)
CHG$CCat04 <- rvlabel(CHG$CCat04)
CHG$CCat03 <- rvlabel(CHG$CCat03)
JUD$JCat12 <- rvlabel(JUD$JCat12)
JUD$JCat10 <- rvlabel(JUD$JCat10)
JUD$JCat04 <- rvlabel(JUD$JCat04)
JUD$JCat03 <- rvlabel(JUD$JCat03)
```

\FloatBarrier

## Additional Data Files
We may or may not need these additional data files. We will come back and edit 
this section later to remove anything we don't need. See Campbell (2019) for 
details on these files. 

``` {r import_other}
# Read SPSS data files.
ESC <- read_sav("data/ESCALATIONdata_2018-05-15.sav", user_na = TRUE)
FOR <- read_sav("data/Forensic_Outcomes_2018-04-03.sav", user_na = TRUE)
PER <- read_sav("data/PERPdata_2018-04-03.sav", user_na = TRUE)
SPD <- read_sav("data/SAK_PERP_2018-04-03.sav", user_na = TRUE)
SAK <- read_sav("data/SAKdata_2018-04-03.sav", user_na = TRUE) 
```


********************************************************************************
# Wrap Up

\FloatBarrier

## Project Information
These materials are scholarly products based on research funded by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (01/01/2015–12/31/2018). Serial sexual
assaults: A longitudinal examination of offending patterns using DNA evidence.
[NIJ Award # 2014-NE-BX-0006, Awarded, $699,533]. Sponsor: National Institute of
Justice. Location: Michigan State University, East Lansing, MI.

\FloatBarrier

## References
Campbell, R. (2019). *Serial sexual assaults: A longitudinal examination of
offending patterns using DNA evidence, Detroit, Michigan, 2009* [Data files,
codebooks, computer programs, and statistical output]. ICPSR37134-v1. Ann Arbor,
MI: Inter-university Consortium for Political and Social Research [distributor],
2019-02-28. Retrieved from: https://doi.org/10.3886/ICPSR37134.v1


\FloatBarrier

## Document Information
Folder: *`r getwd()`*

* Script: *`r knitr:::current_input()`*
* Output: *`r sub(".Rmd", ".pdf", knitr:::current_input())`*

\FloatBarrier

## Software Information
We use R Markdown to enhance reproducibility. Knitting the R Markdown script
generates the PDF file containing explanatory text, R code, plus R output 
(text and graphics) noted in the Document Information section above.

- We use [RStudio (version 1.2.5033 or later)](www.rstudio.org) to work with 
  R and R markdown files. The software chain looks like this:
  **Rmd file -> RStudio -> R -> knitr -> pandoc -> MiKTeX -> PDF file**.
- We recommend using [TinyTeX](https://yihui.org/tinytex/) to compile LaTeX files 
  into PDF files. However, it should be viable to use 
  [MiKTeX version 2.9](https://miktex.org) instead. 
  

``` {r show_citations}
sessionInfo()
citation("here")
citation("dplyr")
citation("tidyr")
citation("rmarkdown")
citation("knitr")
citation("kableExtra")
citation("sjlabelled")
citation("haven")
citation("piercer")
```
