---
title: \sffamily{\bfseries{\LARGE Criminal History Records Paper Step 1 (Data Management)}}
geometry: "left=.5in,right=.5in,top=.75in,bottom=.75in"
author: "Steven J. Pierce"
output:
 pdf_document:
   latex_engine: xelatex
   number_sections: true
   toc: yes
   toc_depth: 3
   includes:
     in_header: "../compact-title.tex"
urlcolor: blue
header-includes:
- \usepackage{fancyhdr}
- \usepackage[yyyymmdd,hhmmss]{datetime}
- \usepackage{lastpage}
- \usepackage{fontspec}
- \defaultfontfeatures{Ligatures=TeX}
- \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
- \usepackage{url}
- \usepackage{floatrow}
- \floatplacement{figure}{!ht}
- \floatplacement{table}{!ht}
- \usepackage{placeins}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{dcolumn}
- \usepackage{titling}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}}
- \pagestyle{fancy}
- \lhead{SSA CHR Paper Step 1 Data Mgt}
- \rhead{\today\ \currenttime}
- \lfoot{\texttt{\small \detokenize{`r sub(".Rmd", ".pdf", knitr:::current_input(dir = FALSE))`}}} 
- \cfoot{ }
- \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0.4pt}
- \renewcommand{\footrulewidth}{0.4pt}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

********************************************************************************  
\FloatBarrier

# Purpose.
This file imports copies of publicly archived data files (Campbell, 2019) into 
R, then performs data management to prepare a new data file for a descriptive 
paper about the criminal histories of suspected serial sexual offenders.  


\FloatBarrier

# Setup
Set global R chunk options (local chunk options will over-ride global options). 

``` {r global_options}
# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE)
```

If you have not already done so, install the piercer package from 
[GitHub](https://github.com/sjpierce/piercer) by running the next chunk of R 
code. The chunk is set to eval = FALSE so that you have to manually run that 
code, which you should only need to do once (or whenever the piercer package 
has been updated). 

```{r, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("sjpierce/piercer")
```

Load R packages that we need to get additional functions. 

``` {r load_packages}
library(here)         # for here()
library(dplyr)        # for %>%, filter(), group_by(), & summarise()
library(tidyr)        # for arrange(), filter(), group_by(), mutate(), spread(), 
                      # summarise(), %>%, etc. 
library(rmarkdown)    # for render()
library(knitr)        # for kable()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)   # for kable_styling(), add_header_above(), column_spec(),
                      # collapse_rows(), and landscape()
library(sjlabelled) # For set_label(), get_label()
library(haven)      # for read_spss()
library(piercer)    # for DI() and tag_um()
```

\FloatBarrier

# Import Files
The SPSS files we will need to import, plus docmentation about their contents
and relationships between them, are available from an online archive (Campbell,
2019).

\FloatBarrier

## Core Criminal History Files
Import the SPSS data files for the five core types of records comprising
Michigan criminal history records (CHR): offenders (IDN), incidents (INC),
arrest offenses (ARR), prosecutor charges (CHG), and judicial charges (JUD).
These are necessary to compute some new variables we plan to use.

``` {r import_chr}
# Read SPSS data files.
IDN <- read_sav("data/SSA_IDN_Offenders_2018-09-03.sav", user_na = TRUE)
INC <- read_sav("data/SSA_INC_Incidents_Imputed_2018-09-03.sav", user_na = TRUE)
ARR <- read_sav("data/SSA_ARR_Arrests_Imputed_2018-09-03.sav", user_na = TRUE)
CHG <- read_sav("data/SSA_CHG_PA_Charges_Imputed_2018-09-03.sav", 
                user_na = TRUE)
JUD <- read_sav("data/SSA_JUD_Judicial_Charges_Imputed_2018-09-03.sav", 
                user_na = TRUE) 
```


********************************************************************************
# Wrap Up

\FloatBarrier

## Project Information
These materials are scholarly products based on research funded by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (01/01/2015–12/31/2018). Serial sexual
assaults: A longitudinal examination of offending patterns using DNA evidence.
[NIJ Award # 2014-NE-BX-0006, Awarded, $699,533]. Sponsor: National Institute of
Justice. Location: Michigan State University, East Lansing, MI.

\FloatBarrier

## References
Campbell, R. (2019). *Serial sexual assaults: A longitudinal examination of
offending patterns using DNA evidence, Detroit, Michigan, 2009* [Data files,
codebooks, computer programs, and statistical output]. ICPSR37134-v1. Ann Arbor,
MI: Inter-university Consortium for Political and Social Research [distributor],
2019-02-28. Retrieved from: https://doi.org/10.3886/ICPSR37134.v1


\FloatBarrier

## Document Information
Folder: *`r getwd()`*

* Script: *`r knitr:::current_input()`*
* Output: *`r sub(".Rmd", ".pdf", knitr:::current_input())`*

\FloatBarrier

## Software Information
We use R Markdown to enhance reproducibility. Knitting the R Markdown script
generates the PDF file containing explanatory text, R code, plus R output 
(text and graphics) noted in the Document Information section above.

- We use [RStudio (version 1.2.5033 or later)](www.rstudio.org) to work with 
  R and R markdown files. The software chain looks like this:
  **Rmd file -> RStudio -> R -> knitr -> pandoc -> MiKTeX -> PDF file**.
- We recommend using [TinyTeX](https://yihui.org/tinytex/) to compile LaTeX files 
  into PDF files. However, it should be viable to use 
  [MiKTeX version 2.9](https://miktex.org) instead. 
  

``` {r show_citations}
sessionInfo()
citation("here")
citation("dplyr")
citation("tidyr")
citation("rmarkdown")
citation("knitr")
citation("kableExtra")
citation("sjlabelled")
citation("haven")
citation("piercer")
```
