---
title: \sffamily{\bfseries{\LARGE Criminal History Records Paper Step 2 (Analysis)}}
geometry: "left=.5in,right=.5in,top=.75in,bottom=.75in"
author: "Steven J. Pierce"
output:
 pdf_document:
   latex_engine: xelatex
   number_sections: true
   toc: yes
   toc_depth: 3
   includes:
     in_header: "compact-title.tex"
urlcolor: blue
header-includes:
- \usepackage{fancyhdr}
- \usepackage[yyyymmdd,hhmmss]{datetime}
- \usepackage{lastpage}
- \usepackage{fontspec}
- \defaultfontfeatures{Ligatures=TeX}
- \usepackage[font={small}, margin=1cm, skip=2pt]{caption}
- \usepackage{url}
- \usepackage{floatrow}
- \floatplacement{figure}{!ht}
- \floatplacement{table}{!ht}
- \usepackage{placeins}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{dcolumn}
- \usepackage{titling}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \pretitle{\begin{center}\LARGE\bfseries}
- \posttitle{\end{center}}
- \pagestyle{fancy}
- \lhead{SSA CHR Paper Step 2 Analysis}
- \rhead{\today\ \currenttime}
- \lfoot{\texttt{\small \detokenize{`r sub(".Rmd", ".pdf", knitr:::current_input(dir = FALSE))`}}} 
- \cfoot{ }
- \fancyfoot[R]{\thepage\ of \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0.4pt}
- \renewcommand{\footrulewidth}{0.4pt}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

********************************************************************************  
\FloatBarrier

# Purpose.
This file produces the analysis output required for the paper based on 
Campbell's (2019), after data management teps performed by another script in 
this package. 

\FloatBarrier

# Setup
Set global R chunk options (local chunk options will over-ride global options). 
The method for creating a size option that controls font size in code chunks and
their text output is based on an answer to a question posted on   
[stackoverflow.com](https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex/46526740#46526740). 

``` {r global_options, cfsize = "footnotesize"}
# Create a custom chunk hook/option for controlling font size in chunk & output.
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$cfsize != "normalsize", paste0("\n \\", options$cfsize,"\n\n", 
                                              x, "\n\n \\normalsize"), x)
  })

# Global chunk options (over-ridden by local chunk options)
knitr::opts_chunk$set(include  = TRUE, echo = TRUE, error = TRUE, 
                      message = TRUE, warning = TRUE, cfsize = "footnotesize")
```

Load R packages that we need to get additional functions. 

``` {r load_packages}
library(here)             # for here()
library(plyr)             # For mapvalues()
library(dplyr)            # for %>%, filter(), group_by(), & summarise()
library(tidyr)            # for arrange(), filter(), group_by(), mutate(),  
                          # spread(), summarise(), %>%, etc. 
library(rmarkdown)        # for render()
library(knitr)            # for kable()
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)       # for kable_styling(), add_header_above(), column_spec(),
                          # collapse_rows(), and landscape()
library(descr)            # For freq().
options(descr.plot=FALSE) # Make freq() & crosstab() skip plots by default.
library(lubridate)        # For date conversion, eg. ymd(), time_length().
library(sjlabelled)       # For set_label(), get_label()
library(haven)            # for read_spss()
library(lattice)          # For xyplot(), bwplot(), etc. 
library(psych)            # For describe()
library(car)              # For recode()
library(SSACHR)           # for rvlabel()
```

Create objects to hold settings we plan to reuse often. 

```{r my_settings}
# Custom settings for use with bwplot().
my.boxes <- list(box.rectangle = list(col = "black", lwd = 2), 
                 box.umbrella = list(col = "black", lwd = 2))
```

\FloatBarrier

# Load Data 
The chunk below loads the data saved by the prior script *Step_01_Data_Mgt.Rmd*.

```{r load_data}
load(file = here::here("./data/CHR_Data.RData"))
```

\FloatBarrier

# Offender-Level Summaries
We have few offender-level demographic variables that are worth reporting (we 
will omit summarizing height, weight, hair color, & eye color). After examining
sex, race, and age, we switch focus to looking at descriptive data about the 
criminal history records for arrests, prosecutor charges, and adjudicated 
charges. 

All the CHR summaries in this section focus on variables that have been 
aggregated to offender level. That is why the sample size for all of these
variables is N = `r nrow(IDNEW)` (the number of offenders for whom Michigan CHR 
data were available and the start date for the earliest SAK testing window could
be established). 

\FloatBarrier

## Sex
```{r examine_Sex}
kable(freq(as_factor(IDNEW$Sex)), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Offender Sex")
```

\FloatBarrier

## Race
```{r examine_Race}
kable(freq(as_factor(IDNEW$Race), user.missing = "Unknown"), format = "latex", 
      booktabs = TRUE,  digits = 2, caption = "Offender Race")
```

\FloatBarrier

## Age (as of 04/15/2016)
```{r examine_Age, fig.height = 2}
CNums  <- c(2:4,8,9,11:12, 14:16)
CNames <- c("N", "Mean", "SD", "Min", "Max", "Skew", "Kurtosis", "Q25", "Q50", 
            "Q75")
Age <- describe(IDNEW$Age,  quant=c(.25, .50, .75))
kable(Age[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender Age (as of 04/15/2016)")
bwplot(~ Age, data = IDNEW, factor = 9, xlim = c(18, 82),
       panel = panel.mybox, par.settings = my.boxes,
       xlab = "Offender Age (as of 04/15/2016)")
```

\FloatBarrier

## CHR Record Counts
We aggregated data to count how many CHR records of each type are associated 
with each offender. We summarize the resulting variables (NINC, NARR, NCHG, 
NJUD, & NCON) below.

```{r describe_rcvars}
TCap <- paste("Offender-Level Record Counts (All Crime Categories, Overall and",
              "By When Incident Occured Relative to Testing Window)")
BDA <- c("...Before", "...During", "...After")
rclabs <- c("No. of incidents", BDA, 
            "No. of arrest offenses", BDA,
            "No. of prosecutor charges", BDA,
            "No. of adjudicated charges (all)", BDA,
            "No. of adjudicated charges (convictions)", BDA)

# Summarize CHR record counts (both overall and broken down by IWhen).
IDNEW %>% 
  select(NINC, NINC_Before, NINC_During, NINC_After, 
         NARR, NARR_Before, NARR_During, NARR_After,
         NCHG, NCHG_Before, NCHG_During, NCHG_After,
         NJUD, NJUD_Before, NJUD_During, NJUD_After,
         NCON, NCON_Before, NCON_During, NCON_After) %>% 
  describe(., quant=c(.25, .50, .75)) %>% 
  bind_cols(data.frame(Variable = rclabs), .) %>% 
  select(Variable, n, mean, sd, min, max, skew, kurtosis, Q0.25, Q0.5, Q0.75) %>% 
  kable(., format = "latex", booktabs = TRUE, digits = 2, row.names = FALSE, 
        col.names = c("Variable", CNames), caption = TCap) %>% 
  group_rows(" ", 1, 4) %>% 
  group_rows(" ", 5, 8) %>% 
  group_rows(" ", 9, 12) %>% 
  group_rows(" ", 13, 16) %>% 
  group_rows(" ", 17, 20)
```

kable(freq(IDNEW$NINC), format = "latex", booktabs = TRUE, digits = 2, 
      caption = "Number of Incidents (All Crime Categories)")
```

```{r}
# Get side-by side frequency tables.
```{r freq_NINC}

IDNEW %>% 
  group_by(NINC) %>% 
  count() %>% 
  rename(Value = NINC, n_all = n) -> 
  tmp1
IDNEW %>% 
  group_by(NINC_Before) %>% 
  count() %>% 
  rename(Value = NINC_Before, n_before = n) -> 
  tmp2
IDNEW %>% 
  group_by(NINC_During) %>% 
  count() %>% 
  rename(Value = NINC_During, n_during = n) -> 
  tmp3
IDNEW %>% 
  group_by(NINC_After) %>% 
  count() %>% 
  rename(Value = NINC_After, n_after = n) -> 
  tmp4

tmp1 %>% 
  full_join(tmp2, by = "Value") %>% 
  full_join(tmp3, by = "Value") %>%
  full_join(tmp4, by = "Value") %>% 
  arrange(Value) %>% 
  replace_na(replace = list(n_all = 0, n_before = 0, n_during = 0, n_after = 0))
```




```{r}
kable(freq(IDNEW$NARR), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Number of Arrest Offenses (All Crime Categories)")
```

```{r}
kable(freq(IDNEW$NCHG), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Number of Prosecutor Charges (All Crime Categories)")
```

```{r}
kable(freq(IDNEW$NJUD), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Number of Adjudicated Charges (All Crime Categories, All Dispositions)")
```

```{r}
kable(freq(IDNEW$NCON), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Number of Adjudicated Charges (All Crime Categories, Convictions)")
```

```{r , fig.height = 3}
# Rearrange data so we can easily plot multiple variables. 
IDNW <- gather(data = IDNEW[, c("OID", "NINC", "NARR", "NCHG", "NJUD")], 
               key = VName, value = Count, NINC:NJUD)
IDNW$VName <- ordered(IDNW$VName, levels = c("NINC", "NARR", "NCHG", "NJUD"), 
                      labels = c("Incidents", "Arrest Offenses", 
                                 "Prosecutor Charges", "Adjudicated Charges"))
bwplot(VName ~ Count, data = IDNW, factor = 1, xlim = c(-4, 64),
       panel = panel.mybox, par.settings = my.boxes,
       xlab = "Number of Records for Individual Offender")
densityplot(~ Count | VName, data = IDNW, layout = c(4,1), 
            panel = panel.mydensity, jitter.amount = 0.005,
            strip = strip.custom(par.strip.text = list(cex = .7)),
            xlab = "Number of Records for Individual Offender")
rm(IDNW)
```

\FloatBarrier

## Crime Category Count
Here we are summarizing how many of 12 different categories of crime each 
offender was *arrested for*, *charged with*, and *convicted of* according to 
the CHR data. This sums a set of binary transforms on the incident count 
variables associated with each crime category in ACat12, CCat12, and JCat12. The
*Excluded user-missing* value is not counted as a category, so the possible
range of values for this count is 0-12.

```{r}
CCC <- describe(IDNEW[, c("ACat12_Count", "CCat12_Count", "JCat12_Count")],
                quant=c(.25, .50, .75))
RN.CCC <- c("Crime category count (arrested)", 
            "Crime category count (charged)", 
            "Crime category count (convicted)")
row.names(CCC) <- RN.CCC
kable(CCC[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Crime Category Counts")
```

```{r}
kable(freq(IDNEW$ACat12_Count), format = "latex", booktabs = TRUE, digits = 2, 
      caption = "Crime Category Count (With Arrests)")
```

```{r}
kable(freq(IDNEW$CCat12_Count), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Crime Category Count (With Charges)")
```

```{r}
kable(freq(IDNEW$JCat12_Count), format = "latex", booktabs = TRUE, digits = 2,
      caption = "Crime Category Count (With Convictions)")
```

\FloatBarrier

## Incident Counts by Crime Category (12 levels)
In this section, we analyze variables that contain the number of unique 
incidents in the offender's criminal history for a given type of crime. We have three separate counts for each category of crime, representing incidents where 
the offender was *arrested for*, *charged with*, or *convicted of* crimes  
classified into that category. Note that these variables were created by first
aggregating ARR, CHG, and JUD records to the incident level to flag incidents
that fit the relevant category, then aggregated again to get to the offender
level. It is possible to have multiple arrest offense records, charge records, 
or adjudication records for convictions on a single incident, but these 
variables ignore that and only count each incident once. 

\FloatBarrier

### Arson 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* arson.

```{r}
RN.ACC <- c("Incident count (arrested)", 
            "Incident count (charged)", 
            "Incident count (convicted)")
ACat12_1 <- describe(IDNEW[, c("ACat12_1", "CCat12_1", "JCat12_1")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_1) <- RN.ACC
kable(ACat12_1[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Arson Incident Counts")
```

\FloatBarrier

### Assault - DV, Stalking 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* assaults involving domestic
violence and/or stalking.

```{r}
ACat12_2 <- describe(IDNEW[, c("ACat12_2", "CCat12_2", "JCat12_2")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_2) <- RN.ACC
kable(ACat12_2[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Assault - DV, Stalking Incident Counts")
```

\FloatBarrier

### Assault - Non-Sexual, Non-DV 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* assaults that were non-sexual
and did not involve domestic violence. 

```{r}
ACat12_3 <- describe(IDNEW[, c("ACat12_3", "CCat12_3", "JCat12_3")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_3) <- RN.ACC
kable(ACat12_3[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Assault - Non-Sexual, Non-DV Incident Counts")
```

\FloatBarrier

### Burglary 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* burglary.

```{r}
ACat12_4 <- describe(IDNEW[, c("ACat12_4", "CCat12_4", "JCat12_4")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_4) <- RN.ACC
kable(ACat12_4[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Burglary Incident Counts")
```

\FloatBarrier

### Criminal Sexual Conduct
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* criminal sexual conduct.

Note: We actually have redundant sets of variables that contain these particular
counts. The variables OCSC1-OCSC3 were created and stored in the SPSS file; the
variables ACat12_5, CCat12_5, and JCat12_5 contain exactly the same data, but 
were created above in the **Aggregating Crime Category Variables** section. 

```{r}
CSC <- describe(IDNEW[, c("OCSC1", "OCSC2", "OCSC3")], quant=c(.25, .50, .75))
kable(CSC[, CNums], digits = 2, format = "latex", booktabs = TRUE, 
      col.names = CNames,
      caption = "Offender-Level Criminal Sexual Conduct Incident Counts")
```

```{r}
kable(freq(IDNEW$OCSC1), digits = 2, format = "latex", booktabs = TRUE, 
      caption = "Criminal Sexual Conduct Incident Count (With Arrests)")
```

```{r}
kable(freq(IDNEW$OCSC2), digits = 2, format = "latex", booktabs = TRUE, 
      caption = "Criminal Sexual Conduct Incident Count (With Charges)")
```

```{r}
kable(freq(IDNEW$OCSC3), digits = 2, format = "latex", booktabs = TRUE, 
      caption = "Criminal Sexual Conduct Incident Count (With Convictions)")
```

```{r}
# Check how many offenders had > 1 CSC arrest, > 1 CSC charge, and/or > 1 CSC 
# conviction in their CHR data. 
nrow(IDNEW[with(IDNEW, OCSC1 > 1 | OCSC2 > 1 | OCSC3 > 1),]) 
```

```{r , fig.height = 3, warning= FALSE}
# Rearrange data so we can easily plot multiple variables. 
IDNW <- gather(data = IDNEW[, c("OID", "OCSC1", "OCSC2", "OCSC3")], 
               key = VName, value = Count, OCSC1:OCSC3)
IDNW$VName <- ordered(IDNW$VName, levels = c("OCSC1", "OCSC2", "OCSC3"), 
                      labels = c("Arrests", "Charges", "Convictions"))
densityplot(~ Count | VName, data = IDNW, layout = c(3,1), 
            panel = panel.mydensity, jitter.amount = 0.1,
            strip = strip.custom(par.strip.text = list(cex = 1)),
            xlab = "Number of Incidents with Criminal Sexual Conduct")
rm(IDNW)
```

\FloatBarrier

### Drug Crime 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* drug crimes.

```{r}
ACat12_6 <- describe(IDNEW[, c("ACat12_6", "CCat12_6", "JCat12_6")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_6) <- RN.ACC
kable(ACat12_6[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Drug Crime Incident Counts")
```

\FloatBarrier

### Homicide 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* homicide.

```{r}
ACat12_7 <- describe(IDNEW[, c("ACat12_7", "CCat12_7", "JCat12_7")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_7) <- RN.ACC
kable(ACat12_7[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Homicide Incident Counts")
```

\FloatBarrier

### Larceny/Theft/Fraud 
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* larceny, theft, or fraud. 

```{r}
ACat12_8 <- describe(IDNEW[, c("ACat12_8", "CCat12_8", "JCat12_8")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_8) <- RN.ACC
kable(ACat12_8[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Larceny, Theft, or Fraud Incident Counts")
```

\FloatBarrier

### Robbery
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* robbery.

```{r}
ACat12_9 <- describe(IDNEW[, c("ACat12_9", "CCat12_9", "JCat12_9")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_9) <- RN.ACC
kable(ACat12_9[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Robbery Incident Counts")
```

\FloatBarrier

### Sex Crimes
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* sex crimes (excluding 
criminal sexual conduct).

```{r}
ACat12_10 <- describe(IDNEW[, c("ACat12_10", "CCat12_10", "JCat12_10")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_10) <- RN.ACC
kable(ACat12_10[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Sex Crime Incident Counts")
```

\FloatBarrier

### Traffic and Ordinances
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* traffic crimes and violations
of ordinances.

```{r}
ACat12_11 <- describe(IDNEW[, c("ACat12_11", "CCat12_11", "JCat12_11")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_11) <- RN.ACC
kable(ACat12_11[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Traffic and Ordinance Incident Counts")
```

\FloatBarrier

### Weapons
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* weapons crimes.

```{r}
ACat12_12 <- describe(IDNEW[, c("ACat12_12", "CCat12_12", "JCat12_12")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_12) <- RN.ACC
kable(ACat12_12[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Weapons Incident Counts")
```

\FloatBarrier

### Other Crimes (Excluded User-Missing)
Here we summarize the counts of unique incidents where the offender was 
*arrested for*, *charged with*, and *convicted of* any other type of crime not
included in the other tables above this section.

```{r}
ACat12_999 <- describe(IDNEW[, c("ACat12_999", "CCat12_999", "JCat12_999")], 
                  quant=c(.25, .50, .75))
row.names(ACat12_999) <- RN.ACC
kable(ACat12_999[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender-Level Other Crime (Excluded User-Missing) Incident Counts")
```

********************************************************************************
\FloatBarrier

# Arrest Offense Record Summaries
All summaries in this section directly summarize the ARR data without first 
aggregating to the incident or offender level. 

\FloatBarrier

## Crime Category (12 levels)
```{r}
kable(freq(as_factor(ARREW$ACat12), user.missing = "Excluded user-missing"), 
      format = "latex", booktabs = TRUE, digits = 2, 
      format.args = list(big.mark = ','),
      caption = "Number of Arrest Offense Records by Crime Category (12 levels)")
```

\FloatBarrier

## Age at Arrest for Criminal Sexual Conduct
```{r}
OAgeA <- describe(ARREW[ARREW$ACat12 == 5, "OAgeA"],  quant=c(.25, .50, .75))
kable(OAgeA[, CNums], format = "latex", booktabs = TRUE, digits = 2, 
      col.names = CNames,
      caption = "Offender Age at Arrest for Criminal Sexual Conduct")
```

********************************************************************************
\FloatBarrier

# Prosecutor Charge Record Summaries
All summaries in this section directly summarize the CHG data without first 
aggregating to the incident or offender level. 

\FloatBarrier

## Crime Category (12 levels)
```{r, fig.height = 2}
kable(freq(as_factor(CHGEW$CCat12), user.missing = "Excluded user-missing"), 
      format = "latex", booktabs = TRUE, digits = 2, 
      format.args = list(big.mark = ','),
      caption = "Number of Prosecutor Charge Records by Crime Category (12 levels)")
```

********************************************************************************
\FloatBarrier

# Judicial Charge Record Summaries
All summaries in this section directly summarize the JUD data without first 
aggregating to the incident or offender level. Note that here we do not
distinguish between adjudicated charge records based on disposition. While
some of these records are convictions, others will have other dispositions.

\FloatBarrier

## Crime Category (12 levels, all dispositions)
```{r, fig.height = 2}
kable(freq(as_factor(JUDEW$JCat12), user.missing = "Excluded user-missing"), 
      format = "latex", booktabs = TRUE, digits = 2, 
      format.args = list(big.mark = ','),
      caption = "Number of Adjudicated Charge Records (All Dispositions) by Crime Category (12 levels)")
```

\FloatBarrier

## Crime Category (12 levels, convictions)
```{r, fig.height = 2}
kable(freq(as_factor(JUDEW$JCat12[JUDEW$JDispCat == 1]), 
           user.missing = "Excluded user-missing"), 
      format = "latex", booktabs = TRUE, digits = 2, 
      format.args = list(big.mark = ','),
      caption = "Number of Adjudicated Charge Records (Convictions Only) by Crime Category (12 levels)")
```

********************************************************************************
# Wrap Up

\FloatBarrier

## Project Information
These materials are scholarly products based on research funded by the following 
grant. 

Campbell, R., Pierce, S. J., & Sharma, D. (01/01/2015–12/31/2018). Serial sexual
assaults: A longitudinal examination of offending patterns using DNA evidence.
[NIJ Award # 2014-NE-BX-0006, Awarded, $699,533]. Sponsor: National Institute of
Justice. Location: Michigan State University, East Lansing, MI.

\FloatBarrier

## References
Campbell, R. (2019). *Serial sexual assaults: A longitudinal examination of
offending patterns using DNA evidence, Detroit, Michigan, 2009* [Data files,
codebooks, computer programs, and statistical output]. ICPSR37134-v1. Ann Arbor,
MI: Inter-university Consortium for Political and Social Research [distributor],
2019-02-28. Retrieved from: https://doi.org/10.3886/ICPSR37134.v1

\FloatBarrier

## Software Information
We use R Markdown to enhance reproducibility. Knitting the source R Markdown 
script *`r knitr:::current_input()`* generates this PDF file containing 
explanatory text, R code, plus R output (text and graphics).

- We used [RStudio](www.rstudio.org) `r rstudioapi::versionInfo()$version` to 
  work with R and R markdown files. The software chain looks like this:
  **Rmd file > RStudio > R > rmarkdown > knitr > pandoc > TinyTeX or MiKTeX > PDF file**.
- We recommend using [TinyTeX](https://yihui.org/tinytex/) to compile LaTeX files 
  into PDF files. However, it should be viable to use 
  [MiKTeX version 2.9](https://miktex.org) instead. 
- We used [pandoc](https://pandoc.org) `r pandoc_version()` for this 
  document. 

This document was generated using the following computational environment and 
dependencies: 

``` {r show_citations}
# If is_tineytex = TRUE, then we used TinyTex, otherwise we used MikTeX. 
tinytex:::is_tinytex()

# Get R and R package version numbers in use.
devtools::session_info()
```

The current Git commit details and status are:

```{r git_details, eval=TRUE}
# Store whether git2r is installed and we are in a git repository.
GitCheck <- "git2r" %in% installed.packages() & git2r::in_repository(path = ".")
cat(paste("GitCheck =", GitCheck, "\n"))

# What commit is this file at? 
if (GitCheck) git2r::repository(here::here())

# What is the repository status? 
if (GitCheck) git2r::status()
```
